---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "100%",
  results = "hold",
  comment = "#>"
)
```

# binance

<!-- badges: start -->
[![R-CMD-check](https://github.com/dereckscompany/binance/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dereckscompany/binance/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

**In plain terms:** Binance is one of the largest cryptocurrency exchanges, where people buy, sell and hold digital coins. This package is the R doorway to it: you can pull historical price data and stream live market updates such as the order book, place and manage buy and sell orders on both the spot and futures markets, and handle the account side -- balances, deposits, withdrawals, transfers and sub-accounts -- all from R scripts. Requests can run the ordinary way, where your code waits for each answer, or in the background so your program keeps working and collects the results later. For research it can bulk-download years of price history and resume where it left off if it is interrupted, handing everything back as tidy tables ready for analysis. Because it can move real funds and place real trades, it is built to be driven deliberately and tested with small amounts first.

## Technical overview

An R API wrapper for the [Binance](https://www.binance.com/) cryptocurrency exchange. Provides `R6` classes for spot market data, trading, account management, deposits, withdrawals, and sub-accounts. Supports both synchronous and asynchronous (promise based) operation via `httr2`.

## Disclaimer

This software is provided "as is", without warranty of any kind. **This package interacts with live cryptocurrency exchange accounts and can execute real trades, transfers, and withdrawals involving real money.** By using this package you accept full responsibility for any financial losses, erroneous transactions, or other damages that may result. Always test with small amounts first, use API key permissions to restrict access to only what you need, and never share your API credentials. The author(s) and contributor(s) are not liable for any financial loss or damage arising from the use of this software.

We invite you to read the source code and make contributions if you find a bug or wish to make an improvement.

## Design Philosophy

All API responses are returned as `data.table` objects. The package targets a consistent "one entity = one row, no list columns" shape, but the exact transformation is endpoint-specific. See each method's `@return` block for the precise list of columns and any per-endpoint behaviour.

The transformations the parsers apply:

1. **snake_case column names** - camelCase keys from the JSON response (e.g. `insertTime`, `quoteQty`) are converted to snake_case (`insert_time`, `quote_qty`). A handful of endpoints additionally rename for clarity (e.g. nested objects are wide-prefixed to `parent_child` columns; collapsed array fields land under the plural form like `permissions`).

2. **Type coercion** for well-known columns - millisecond timestamps become `POSIXct`; selected nested numeric `filters` are extracted into flat `lot_min_qty` / `price_tick_size` / `min_notional` columns.

3. **Shape normalisation** for nested arrays and objects, applied per endpoint:
    - **Arrays of plain strings** (e.g. `orderTypes`, `permissions`, `allowedSelfTradePreventionModes`) → collapsed into one `;`-separated character column. Recover via `strsplit(x, ";", fixed = TRUE)[[1]]`.
    - **Arrays of objects with a fixed schema** (e.g. order `fills`, account `assets`, OCO `orderReports`, sub-account `spotSubUserAssetBtcVoList`) → exploded to long format with parent fields replicated and a `<child>_` prefix on the child columns. A 1-indexed position column is added where order matters.
    - **Single nested objects with a fixed schema** (e.g. account `commissionRates`, locked-earn `detail` / `quota`) → flattened to wide `parent_child` columns.
    - **Nested objects with dynamic keys** (e.g. spot exchange-info `permissionSets`, flexible-earn `tierAnnualPercentageRate`) → serialised as a JSON string column so the inner structure is preserved; recover via `jsonlite::fromJSON(x)`.

**Endpoints that reshape rather than drop:**

The parsers never discard API data — every field is either on the row, on a sibling row, on a sibling method's return, or attached as an attribute on the returned `data.table`.

- `get_account_info()` (spot) - account-level fields are returned as a single row; the companion `balances` array is parsed by the sibling `get_balances()` (both methods hit `/api/v3/account` and parse different halves).
- `get_account()` (futures) - one row per asset balance; the companion `positions` array is parsed by the sibling `get_positions()` (which hits `/fapi/v2/positionRisk`).
- `get_exchange_info()` (spot and futures) - one row per symbol. The full per-symbol `filters` array is preserved as a JSON-encoded `filters_raw` column alongside the curated `lot_*` / `price_*` / `min_notional` columns (recover with `jsonlite::fromJSON(dt$filters_raw[1])`). Exchange-wide blocks (rate limits, exchange-wide filter rules, and on futures the margin-asset config) are exposed via sibling methods on the same class: `get_rate_limits()`, `get_exchange_filters()`, and (futures only) `get_futures_assets()`. `serverTime` is the long-standing `get_server_time()`. The constants (`timezone = "UTC"`, `futuresType = "U_M"`) are not re-exposed.
- The OCO endpoints (`add_oco_order()`, `cancel_oco_order()`) expand the richer `orderReports` payload; the thinner `orders` duplicate is a strict subset of the same data and so is omitted.

**Klines** are a special case: Binance returns positional arrays instead of named objects, so we assign descriptive column names (`open_time`, `open`, `high`, `low`, `close`, `volume`, `close_time`, etc.) matching the Binance documentation.

If a column you expect is missing, check the method's `@return`; if it still looks wrong, please file an issue.

## Available Classes

| Class | Purpose | Auth Required |
|-------|---------|:---:|
| `BinanceMarketData` | Spot market data: tickers, klines, depth, trades, exchange info | No |
| `BinanceTrading` | Spot order placement, query, and cancellation | Yes |
| `BinanceOcoOrders` | One-Cancels-Other order management | Yes |
| `BinanceAccount` | Account info and trade history | Yes |
| `BinanceDeposit` | Deposit addresses and deposit history | Yes |
| `BinanceWithdrawal` | Withdrawal submission and history | Yes |
| `BinanceTransfer` | Internal transfers between wallet types (spot, margin, futures) | Yes |
| `BinanceSubAccount` | Sub-account listing and management | Yes |
| `BinanceEarn` | Simple Earn: flexible savings products and positions | Yes |
| `BinanceMarginData` | Margin pairs, price index, interest rates, cross/isolated data | Mixed |
| `BinanceMargin` | Margin borrowing, repayment, orders, and account queries | Yes |
| `BinanceFuturesData` | Futures exchange info, mark price, funding rates, klines | No |
| `BinanceFutures` | Futures order placement, positions, leverage, account queries | Yes |
| `BinanceMarketStream` | Live spot market-data WebSocket streams (order-book depth) | No |
| `BinanceBase` | Internal base class (not used directly) | — |
| `BinanceWsBase` | Internal base class for WebSocket streams (not used directly) | — |

All REST classes accept an `async = TRUE` argument at construction and share a common `time_source` parameter for clock drift correction. The WebSocket classes are always event-driven (a socket is an endless push stream, not a single request) — see [WebSocket Streams](#websocket-streams) below.

## Installation

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("dereckscompany/binance")
```

## Setup

```{r}
# special mock for local build
box::use(
  binance[
    get_api_keys,
    get_futures_base_url
  ],
  ./tests/testthat/mock_router[mock_router]
)

KEYS <- get_api_keys(
  api_key = "fake-key",
  api_secret = "fake-secret"
)

BASE <- "https://api.binance.com"
FBASE <- "https://fapi.binance.com"

options(httr2_mock = mock_router)

# normal imports
box::use(
  binance[
    BinanceMarketData,
    BinanceTrading,
    BinanceAccount,
    BinanceMargin,
    BinanceFutures,
    BinanceFuturesData
  ]
)
```

Set your API credentials as environment variables in `.Renviron`:

```bash
BINANCE_API_ENDPOINT = "https://api.binance.com"
BINANCE_API_KEY = your-api-key
BINANCE_API_SECRET = your-api-secret
```

If you don't have a key, visit the [Binance API documentation](https://developers.binance.com/docs/binance-spot-api-docs).

## Quick Start -- Market Data

Market data endpoints are public and require no authentication.

```{r}
market <- BinanceMarketData$new(keys = KEYS, base_url = BASE)
```

### Price Ticker

```{r}
market$get_ticker(symbol = "BTCUSDT")
```

### Klines (Candlestick Data)

```{r}
market$get_klines(symbol = "BTCUSDT", interval = "1h", limit = 5)
```

### Fetch All Klines (Large Date Ranges)

When you need more than 1000 candles, pass `fetch_all = TRUE`. The method pages forward through the range — following the data and stopping at the first empty or short page — and returns the combined result. Because Binance returns candles from the first one on or after `start_time`, an empty leading stretch (e.g. dates before a symbol was listed) is skipped in a single request:

```{r}
all_klines <- market$get_klines(
  symbol = "BTCUSDT",
  interval = "1h",
  start_time = lubridate::as_datetime("2024-01-01", tz = "UTC"),
  end_time = lubridate::as_datetime("2024-06-01", tz = "UTC"),
  fetch_all = TRUE,
  sleep = 0
)
nrow(all_klines)
```

Pass an `on_page` callback to **stream** each page as it is fetched instead of holding the whole result in memory — the method then returns invisibly and your callback owns the data (this is how `binance_backfill_klines()` writes to disk page by page):

```{r}
candles <- 0L
market$get_klines(
  symbol = "BTCUSDT", interval = "1h",
  start_time = lubridate::as_datetime("2024-01-01", tz = "UTC"),
  end_time = lubridate::as_datetime("2024-02-01", tz = "UTC"),
  fetch_all = TRUE,
  on_page = function(page) candles <<- candles + nrow(page)
)
candles
```

> **Note:** Large date ranges consume multiple API requests. Use the `sleep` parameter to avoid hitting Binance rate limits. For bulk multi-symbol downloads, see `binance_backfill_klines()`.

### Order Book Depth

```{r}
market$get_depth(symbol = "BTCUSDT", limit = 5)
```

### 24hr Statistics

```{r}
market$get_24hr_stats(symbol = "BTCUSDT")
```

## Trading

Trading endpoints require authentication. Use `add_order_test()` to validate order parameters without placing a real order.

```{r}
trading <- BinanceTrading$new(keys = KEYS, base_url = BASE)
```

### Test Order (No Execution)

```{r}
trading$add_order_test(
  type = "LIMIT",
  symbol = "BTCUSDT",
  side = "BUY",
  price = 50000,
  quantity = 0.0001
)
```

### Query an Order

```{r}
trading$get_order(symbol = "BTCUSDT", order_id = 12345)
```

### Get Open Orders

```{r}
trading$get_open_orders(symbol = "BTCUSDT")
```

## Account

```{r}
account <- BinanceAccount$new(keys = KEYS, base_url = BASE)
```

### Account Info

```{r}
account$get_account_info()
```

### Trade History

```{r}
account$get_trades(symbol = "BTCUSDT")
```

## Margin Trading

Margin endpoints use the same credential setup. Here is a brief overview:

```{r}
margin <- BinanceMargin$new(keys = KEYS, base_url = BASE)
```

### Margin Account

```{r}
margin$get_account()
```

### Max Borrowable

```{r}
margin$get_max_borrowable(asset = "USDT")
```

### Margin Trades

```{r}
margin$get_trades(symbol = "BTCUSDT")
```

## Futures

### Futures Market Data

```{r}
fdata <- BinanceFuturesData$new(keys = KEYS, base_url = FBASE)
```

#### Mark Price and Funding Rate

```{r}
fdata$get_mark_price(symbol = "BTCUSDT")
```

#### Funding Rate History

```{r}
fdata$get_funding_rate(symbol = "BTCUSDT", limit = 3)
```

#### Open Interest

```{r}
fdata$get_open_interest(symbol = "BTCUSDT")
```

### Futures Trading

```{r}
futures <- BinanceFutures$new(keys = KEYS, base_url = FBASE)
```

#### Positions

```{r}
futures$get_positions(symbol = "BTCUSDT")
```

#### Futures Test Order

```{r}
futures$add_order_test(
  symbol = "BTCUSDT",
  side = "BUY",
  type = "LIMIT",
  quantity = 0.001,
  price = 50000,
  time_in_force = "GTC"
)
```

#### Set Leverage

```{r}
futures$set_leverage(symbol = "BTCUSDT", leverage = 10)
```

## Async Usage

This package is meant to be used in an asynchronous non-blocking event loop (i.e. à la JavaScript) and is written around promises. Please use `later` to run your event loop. I recommend the pattern shown below.

We offer a synchronous and asynchronous instance of the classes. All classes accept `async = TRUE`, this makes methods return promises instead of objects. You can resolve promises in whichever way you like, either `$then()` chaining or `async`/`await` patterns.

I recommend use `coro::async()` to write sequential looking async code:

```{r}
box::use(coro, later)

market_async <- BinanceMarketData$new(async = TRUE)

main <- coro$async(function() {
  ticker <- await(market_async$get_ticker(symbol = "BTCUSDT"))
  klines <- await(market_async$get_klines(symbol = "BTCUSDT", interval = "1h", limit = 10))

  print(ticker)
  print(klines)
})

main()

while (!later$loop_empty()) {
  later$run_now()
}
```

## WebSocket Streams

Beyond the REST API, the package opens **live market-data WebSocket streams** — most importantly the order-book **diff stream**, the only order-book data Binance does not archive, so it has to be captured as it happens. The client is event-driven, modelled on the Node.js `ws` API: register handlers with `$on()`, then drive R's `later` event loop yourself — the same explicit pattern as the async REST example above.

```{r, eval = FALSE}
box::use(binance[BinanceMarketStream], later)

stream <- BinanceMarketStream$new()

# handlers receive the raw JSON message string
stream$on("open", function(e) message("connected"))
stream$on("message", function(msg) cat(msg, "\n"))

# subscribe to the BTC/USDT order-book diff stream at 100 ms
stream$depth("BTCUSDT", speed = "100ms")

# connect, then drive the event loop explicitly (interrupt to stop)
stream$connect()
while (!later$loop_empty()) {
  later$run_now(0.1) # the timeout makes each tick wait for work, not busy-spin
}
```

`$run()` is a convenience that wraps exactly that connect-and-pump loop and tears down cleanly on an interrupt — reach for it when the stream is the only thing running. Write each raw message straight to an append-only file and you have an order-book recorder; see `vignette("websocket-streams")` for the recorder pattern and reconnection.

## Sample Data

The package ships with a sample dataset of 500 BTC-USDT 4-hour candles for demonstration and testing:

```{r, eval = FALSE}
data(binance_btc_usdt_4h_ohlcv)
head(binance_btc_usdt_4h_ohlcv)
```

See `?binance_btc_usdt_4h_ohlcv` for column descriptions. This data was produced by `binance_backfill_klines()`.

## Citation

If you use this package in your work, please cite it:

```r
citation("binance")
```

> Mezquita, D. (2026). binance: R API Wrapper to Binance Cryptocurrency
> Exchange. R package version 0.0.1.

## Licence

MIT &copy; [Dereck Mezquita](https://github.com/dereckmezquita) [![ORCID](https://img.shields.io/badge/ORCID-0000--0002--9307--6762-green)](https://orcid.org/0000-0002-9307-6762). See [LICENSE](LICENSE) for the full text.
