---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "100%",
  results = "hold",
  comment = "#>"
)
```

# binance

<!-- badges: start -->
[![R-CMD-check](https://github.com/dereckscompany/binance/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dereckscompany/binance/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

An R API wrapper for the [Binance](https://www.binance.com/) cryptocurrency exchange. Provides `R6` classes for spot market data, trading, account management, deposits, withdrawals, and sub-accounts. Supports both synchronous and asynchronous (promise based) operation via `httr2`.

## Disclaimer

This software is provided "as is", without warranty of any kind. **This package interacts with live cryptocurrency exchange accounts and can execute real trades, transfers, and withdrawals involving real money.** By using this package you accept full responsibility for any financial losses, erroneous transactions, or other damages that may result. Always test with small amounts first, use API key permissions to restrict access to only what you need, and never share your API credentials. The author(s) and contributor(s) are not liable for any financial loss or damage arising from the use of this software.

We invite you to read the source code and make contributions if you find a bug or wish to make an improvement.

## Design Philosophy

All API responses are returned as `data.table` objects. The package targets a consistent "one entity = one row, no list columns" shape, but the exact transformation is endpoint-specific. See each method's `@return` block for the precise list of columns and any per-endpoint behaviour.

The transformations the parsers apply:

1. **snake_case column names** - camelCase keys from the JSON response (e.g. `insertTime`, `quoteQty`) are converted to snake_case (`insert_time`, `quote_qty`). A handful of endpoints additionally rename for clarity (e.g. nested objects are wide-prefixed to `parent_child` columns; collapsed array fields land under the plural form like `permissions`).

2. **Type coercion** for well-known columns - millisecond timestamps become `POSIXct`; selected nested numeric `filters` are extracted into flat `lot_min_qty` / `price_tick_size` / `min_notional` columns.

3. **Shape normalisation** for nested arrays and objects, applied per endpoint:
    - **Arrays of plain strings** (e.g. `orderTypes`, `permissions`, `allowedSelfTradePreventionModes`) → collapsed into one `;`-separated character column. Recover via `strsplit(x, ";", fixed = TRUE)[[1]]`.
    - **Arrays of objects with a fixed schema** (e.g. order `fills`, account `assets`, OCO `orderReports`, watchlist children) → exploded to long format with parent fields replicated and a `<child>_` prefix on the child columns. A 1-indexed position column is added where order matters.
    - **Single nested objects with a fixed schema** (e.g. account `commissionRates`, locked-earn `detail` / `quota`) → flattened to wide `parent_child` columns.
    - **Nested objects with dynamic keys** (e.g. spot exchange-info `permissionSets`, flexible-earn `tierAnnualPercentageRate`) → serialised as a JSON string column so the inner structure is preserved; recover via `jsonlite::fromJSON(x)`.

**Endpoints that deliberately drop fields:**

- `get_account_info()` (spot) - the `balances` array is replaced by a separate `get_balances()` call; account-level fields are returned as a single row.
- `get_account()` (futures) - returns one row per asset balance only. The companion `positions` array Binance returns alongside is intentionally dropped; use `get_positions()` for per-position data (it hits `/fapi/v2/positionRisk`).
- `get_exchange_info()` (spot and futures) - the raw `filters` array is dropped after extracting the canonical `lot_*`, `price_*`, and `min_notional` numeric fields. The top-level `rateLimits`, `exchangeFilters`, and (spot) `sors` blocks are also dropped from the one-row-per-symbol return; the per-symbol scalars and arrays remain.
- The OCO endpoints (`add_oco_order()`, `cancel_oco_order()`) expand the richer `orderReports` payload and drop the thinner `orders` duplicate.

**Klines** are a special case: Binance returns positional arrays instead of named objects, so we assign descriptive column names (`open_time`, `open`, `high`, `low`, `close`, `volume`, `close_time`, etc.) matching the Binance documentation.

If a column you expect is missing, check the method's `@return`; if it still looks wrong, please file an issue.

## Available Classes

| Class | Purpose | Auth Required |
|-------|---------|:---:|
| `BinanceMarketData` | Spot market data: tickers, klines, depth, trades, exchange info | No |
| `BinanceTrading` | Spot order placement, query, and cancellation | Yes |
| `BinanceOcoOrders` | One-Cancels-Other order management | Yes |
| `BinanceAccount` | Account info and trade history | Yes |
| `BinanceDeposit` | Deposit addresses and deposit history | Yes |
| `BinanceWithdrawal` | Withdrawal submission and history | Yes |
| `BinanceTransfer` | Internal transfers between wallet types (spot, margin, futures) | Yes |
| `BinanceSubAccount` | Sub-account listing and management | Yes |
| `BinanceEarn` | Simple Earn: flexible savings products and positions | Yes |
| `BinanceMarginData` | Margin pairs, price index, interest rates, cross/isolated data | Mixed |
| `BinanceMargin` | Margin borrowing, repayment, orders, and account queries | Yes |
| `BinanceFuturesData` | Futures exchange info, mark price, funding rates, klines | No |
| `BinanceFutures` | Futures order placement, positions, leverage, account queries | Yes |
| `BinanceBase` | Internal base class (not used directly) | — |

All classes accept an `async = TRUE` argument at construction and share a common `time_source` parameter for clock drift correction.

## Installation

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("dereckscompany/binance")
```

## Setup

```{r}
# special mock for local build
box::use(
  binance[
    get_api_keys,
    get_futures_base_url
  ],
  ./tests/testthat/mock_router[mock_router]
)

KEYS <- get_api_keys(
  api_key = "fake-key",
  api_secret = "fake-secret"
)

BASE <- "https://api.binance.com"
FBASE <- "https://fapi.binance.com"

options(httr2_mock = mock_router)

# normal imports
box::use(
  binance[
    BinanceMarketData,
    BinanceTrading,
    BinanceAccount,
    BinanceMargin,
    BinanceFutures,
    BinanceFuturesData
  ]
)
```

Set your API credentials as environment variables in `.Renviron`:

```bash
BINANCE_API_ENDPOINT = "https://api.binance.com"
BINANCE_API_KEY = your-api-key
BINANCE_API_SECRET = your-api-secret
```

If you don't have a key, visit the [Binance API documentation](https://developers.binance.com/docs/binance-spot-api-docs).

## Quick Start -- Market Data

Market data endpoints are public and require no authentication.

```{r}
market <- BinanceMarketData$new(keys = KEYS, base_url = BASE)
```

### Price Ticker

```{r}
market$get_ticker(symbol = "BTCUSDT")
```

### Klines (Candlestick Data)

```{r}
market$get_klines(symbol = "BTCUSDT", interval = "1h", limit = 5)
```

### Fetch All Klines (Large Date Ranges)

When you need historical data spanning more than 1000 candles, use `fetch_all = TRUE`. This automatically segments the time range into multiple API calls, deduplicates overlapping boundaries, and returns the combined result:

```{r, eval = FALSE}
# Fetch all 1h klines across a 5-month date range (multiple API calls)
market$get_klines(
  symbol = "BTCUSDT",
  interval = "1h",
  startTime = as.POSIXct("2024-01-01", tz = "UTC"),
  endTime = as.POSIXct("2024-06-01", tz = "UTC"),
  fetch_all = TRUE,
  sleep = 0.5
)
```

> **Note:** Large date ranges consume multiple API requests. Use the `sleep` parameter to avoid hitting Binance rate limits. For bulk multi-symbol downloads, see `binance_backfill_klines()`.

### Order Book Depth

```{r}
market$get_depth(symbol = "BTCUSDT", limit = 5)
```

### 24hr Statistics

```{r}
market$get_24hr_stats(symbol = "BTCUSDT")
```

## Trading

Trading endpoints require authentication. Use `add_order_test()` to validate order parameters without placing a real order.

```{r}
trading <- BinanceTrading$new(keys = KEYS, base_url = BASE)
```

### Test Order (No Execution)

```{r}
trading$add_order_test(
  type = "LIMIT",
  symbol = "BTCUSDT",
  side = "BUY",
  price = 50000,
  quantity = 0.0001
)
```

### Query an Order

```{r}
trading$get_order(symbol = "BTCUSDT", orderId = 12345)
```

### Get Open Orders

```{r}
trading$get_open_orders(symbol = "BTCUSDT")
```

## Account

```{r}
account <- BinanceAccount$new(keys = KEYS, base_url = BASE)
```

### Account Info

```{r}
account$get_account_info()
```

### Trade History

```{r}
account$get_trades(symbol = "BTCUSDT")
```

## Margin Trading

Margin endpoints use the same credential setup. Here is a brief overview:

```{r}
margin <- BinanceMargin$new(keys = KEYS, base_url = BASE)
```

### Margin Account

```{r}
margin$get_account()
```

### Max Borrowable

```{r}
margin$get_max_borrowable(asset = "USDT")
```

### Margin Trades

```{r}
margin$get_trades(symbol = "BTCUSDT")
```

## Futures

### Futures Market Data

```{r}
fdata <- BinanceFuturesData$new(keys = KEYS, base_url = FBASE)
```

#### Mark Price and Funding Rate

```{r}
fdata$get_mark_price(symbol = "BTCUSDT")
```

#### Funding Rate History

```{r}
fdata$get_funding_rate(symbol = "BTCUSDT", limit = 3)
```

#### Open Interest

```{r}
fdata$get_open_interest(symbol = "BTCUSDT")
```

### Futures Trading

```{r}
futures <- BinanceFutures$new(keys = KEYS, base_url = FBASE)
```

#### Positions

```{r}
futures$get_positions(symbol = "BTCUSDT")
```

#### Futures Test Order

```{r}
futures$add_order_test(
  symbol = "BTCUSDT",
  side = "BUY",
  type = "LIMIT",
  quantity = 0.001,
  price = 50000,
  timeInForce = "GTC"
)
```

#### Set Leverage

```{r}
futures$set_leverage(symbol = "BTCUSDT", leverage = 10)
```

## Async Usage

This package is meant to be used in an asynchronous non-blocking event loop (i.e. à la JavaScript) and is written around promises. Please use `later` to run your event loop. I recommend the pattern shown below.

We offer a synchronous and asynchronous instance of the classes. All classes accept `async = TRUE`, this makes methods return promises instead of objects. You can resolve promises in whichever way you like, either `$then()` chaining or `async`/`await` patterns.

I recommend use `coro::async()` to write sequential looking async code:

```{r}
box::use(coro, later)

market_async <- BinanceMarketData$new(async = TRUE)

main <- coro$async(function() {
  ticker <- await(market_async$get_ticker(symbol = "BTCUSDT"))
  klines <- await(market_async$get_klines(symbol = "BTCUSDT", interval = "1h", limit = 10))

  print(ticker)
  print(klines)
})

main()

while (!later$loop_empty()) {
  later$run_now()
}
```

## Sample Data

The package ships with a sample dataset of 500 BTC-USDT 4-hour candles for demonstration and testing:

```{r, eval = FALSE}
data(binance_btc_usdt_4h_ohlcv)
head(binance_btc_usdt_4h_ohlcv)
```

See `?binance_btc_usdt_4h_ohlcv` for column descriptions. This data was produced by `binance_backfill_klines()`.

## Citation

If you use this package in your work, please cite it:

```r
citation("binance")
```

> Mezquita, D. (2026). binance: R API Wrapper to Binance Cryptocurrency
> Exchange. R package version 0.0.1.

## Licence

MIT &copy; [Dereck Mezquita](https://github.com/dereckmezquita) [![ORCID](https://img.shields.io/badge/ORCID-0000--0002--9307--6762-green)](https://orcid.org/0000-0002-9307-6762). See [LICENSE.md](LICENSE.md) for the full text, including the citation clause.
