---
title: "Asynchronous Usage with binance"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Asynchronous Usage with binance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

box::use(
  binance[BinanceMarketData, BinanceTrading, BinanceAccount, get_api_keys, get_base_url]
)

box::use(../tests/testthat/mock_router[mock_router])
options(httr2_mock = mock_router)
```

Every R6 class in `binance` accepts an `async = TRUE` flag at construction.
When enabled, all methods return `promises::promise` objects instead of
direct values. This vignette shows how to consume those promises with
`coro::async`/`await` and `later::run_now`.

## Why Async?

Synchronous HTTP blocks the R session while waiting for a reply.
Asynchronous mode lets you fire off multiple requests and process results
as they arrive -- useful for bots that poll several endpoints or place
orders in parallel.

## Setup

```{r load, eval = FALSE}
box::use(
  binance[BinanceMarketData, BinanceTrading, BinanceAccount, get_api_keys],
  coro[async, await],
  later[run_now, loop_empty],
  promises[then, catch, promise_all]
)
```

> **Event loop**: R does not have a built-in event loop like Node.js or
> Python's `asyncio`. Promises only resolve when the event loop ticks via
> `later::run_now()`. In scripts and vignettes, drain the loop with
> `while (!loop_empty()) run_now()`. In **Shiny** apps the event loop runs
> automatically.

---

## Basic Async: `coro::async` + `await`

Pass `async = TRUE` to any class constructor. Methods then return promises
instead of data.tables:

```{r async-basic, eval = FALSE}
market <- BinanceMarketData$new(async = TRUE)

get_ticker <- coro::async(function() {
  ticker <- await(market$get_ticker("BTCUSDT"))
  return(ticker)
})

get_ticker()
while (!later::loop_empty()) later::run_now()
```

> **Key pattern**: define an `async` function, `await` each API call,
> return the result. Drain the event loop with
> `while (!loop_empty()) run_now()`.

---

## Sequential Async: Multiple `await` Calls

Chain several awaited calls in sequence -- each one resolves before the
next begins:

```{r async-sequential, eval = FALSE}
market <- BinanceMarketData$new(async = TRUE)
results <- NULL

fetch_tickers <- coro::async(function() {
  btc <- await(market$get_ticker("BTCUSDT"))
  eth <- await(market$get_ticker("ETHUSDT"))
  results <<- list(btc = btc, eth = eth)
})

fetch_tickers()
while (!later::loop_empty()) later::run_now()
results$btc
results$eth
```

---

## Concurrent Requests with `promise_all`

When requests are independent, fire them simultaneously and collect all
results at once -- the async equivalent of `Promise.all()` in JavaScript:

```{r async-parallel, eval = FALSE}
market <- BinanceMarketData$new(async = TRUE)
results <- NULL

fetch_parallel <- coro::async(function() {
  # Launch both requests concurrently (no await yet)
  btc_promise <- market$get_ticker("BTCUSDT")
  eth_promise <- market$get_ticker("ETHUSDT")

  # Await them together
  res <- await(promises::promise_all(btc = btc_promise, eth = eth_promise))
  results <<- res
})

fetch_parallel()
while (!later::loop_empty()) later::run_now()
results$btc
results$eth
```

---

## Promise Chaining with `then` / `catch`

If you prefer the promise-pipeline style, use `then` and `catch`:

```{r promise-chain, eval = FALSE}
market <- BinanceMarketData$new(async = TRUE)
chain_result <- NULL

market$get_24hr_stats("BTCUSDT") |>
  promises::then(function(stats) {
    chain_result <<- stats
  }) |>
  promises::catch(function(err) {
    message("Error: ", conditionMessage(err))
  })

while (!later::loop_empty()) later::run_now()
chain_result
```

---

## Practical Example: Fetching Multiple Symbols Concurrently

A common use case is polling price data for a watchlist of symbols. With
async mode, all requests fly in parallel rather than sequentially:

```{r multi-symbol, eval = FALSE}
market <- BinanceMarketData$new(async = TRUE)
symbols <- c("BTCUSDT", "ETHUSDT", "SOLUSDT", "BNBUSDT")
all_tickers <- NULL

fetch_watchlist <- coro::async(function() {
  # Fire all requests concurrently
  ticker_promises <- lapply(symbols, function(sym) {
    market$get_ticker(sym)
  })
  names(ticker_promises) <- symbols

  # Await all at once
  res <- await(do.call(promises::promise_all, ticker_promises))
  all_tickers <<- res
})

fetch_watchlist()
while (!later::loop_empty()) later::run_now()

# Each element is a data.table with the ticker result
all_tickers$BTCUSDT
all_tickers$ETHUSDT
```

---

## Running the Event Loop

The critical piece of async R is the **event loop**. Promises do not
resolve until the event loop ticks. In an interactive session or Shiny app,
the event loop runs automatically. In scripts or vignettes, you must drive
it manually.

```r
# Idiomatic event loop drain
while (!later::loop_empty()) later::run_now()
```

Or with a timeout guard:

```r
deadline <- Sys.time() + 30  # 30-second timeout
while (!later::loop_empty() && Sys.time() < deadline) {
  later::run_now(timeoutSecs = 0.1)
}
```

In **Shiny** applications, the event loop is managed for you -- simply
return promises from reactive expressions and Shiny handles resolution.

---

## Error Handling with `tryCatch`

Inside `async` functions, use `tryCatch` around `await` calls for
structured error handling:

```{r async-error, eval = FALSE}
market <- BinanceMarketData$new(async = TRUE)

safe_fetch <- coro::async(function() {
  result <- tryCatch(
    await(market$get_ticker("INVALIDPAIR")),
    error = function(e) {
      message("Caught error: ", conditionMessage(e))
      return(NULL)
    }
  )
  return(result)
})

safe_fetch()
while (!later::loop_empty()) later::run_now()
```

---

## `coro::await` Cheat Sheet

| Pattern | Works? | Notes |
|---------|--------|-------|
| `x <- await(promise)` | Yes | Standard pattern |
| `x <- await(obj$method(arg))` | Yes | Await wrapping a call is fine |
| `await(promise)` (bare, no assignment) | Yes | Side-effect only |
| `await` inside loops/if/tryCatch | Yes | Full control flow support |
| `x <<- await(promise)` | **No** | `<<-` not supported by coro |
| `f(await(promise))` | **No** | Nested inside function args |

> **Rule of thumb**: `await()` must appear as the RHS of a `<-` or as a
> bare statement -- never inside another expression.

---

## Choosing Sync vs Async

| Scenario | Recommendation |
|----------|---------------|
| Interactive exploration | **Sync** -- simpler, results print immediately |
| Scripts fetching one endpoint | **Sync** -- no event loop needed |
| Bots polling multiple symbols | **Async** -- concurrent requests reduce latency |
| Shiny dashboards | **Async** -- keeps the UI responsive |
| Bulk kline downloads | **Sync** -- handle batching in a loop |
