---
title: "Package Tour and Data-Shape Conventions"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package Tour and Data-Shape Conventions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# Docs execute against the synthetic mock router (no network, no keys), so the
# printed shapes are produced by the real parsers from canned fixtures.
box::use(
  binance[
    BinanceMarketData, BinanceAccount, BinanceTrading,
    BinanceFutures, BinanceMargin, BinanceEarn, get_api_keys
  ]
)
box::use(../tests/testthat/mock_router[mock_router])
options(httr2_mock = mock_router)

keys    <- get_api_keys(api_key = "your-key", api_secret = "your-secret")
market  <- BinanceMarketData$new()
acct    <- BinanceAccount$new(keys = keys)
trading <- BinanceTrading$new(keys = keys)
futures <- BinanceFutures$new(keys = keys)
margin  <- BinanceMargin$new(keys = keys)
earn    <- BinanceEarn$new(keys = keys)
```

This vignette is the **one-stop tour** of the `binance` package. It
catalogues every public method by topic, explains the shape of what
each one returns, and then documents the underlying data-shape policy
in detail.

If you've never used the package, read top to bottom. If you've used
it and just want to know how a specific endpoint comes back, jump to
the catalogue table for its class and then to the relevant treatment
section.

The same conventions are shared with the sister `alpaca` and
(in-progress) `kucoin` packages, so that switching between exchanges
does not mean switching mental models of how the data looks.

---

## What's in the package

Thirteen R6 classes cover the spot, futures, margin, Earn,
sub-account, and funding surfaces of the Binance REST API. Every
class supports both **synchronous** and **asynchronous
(promise-based)** operation via `httr2`.

| Class | What it covers |
|---|---|
| `BinanceMarketData` | Spot public market data — server time, exchange info, tickers, 24hr stats, average price, orderbook depth, recent trades, klines |
| `BinanceFuturesData` | USDⓈ-M futures public market data — exchange info, klines, mark price, funding rate, open interest, tickers, orderbook, trades, index/mark-price klines |
| `BinanceMarginData` | Cross- and isolated-margin pair info, price index, interest-rate history, cross/isolated margin data |
| `BinanceTrading` | Spot order management — place, cancel, query (test endpoint included) |
| `BinanceOcoOrders` | Spot OCO (one-cancels-the-other) order placement, cancellation, queries |
| `BinanceFutures` | USDⓈ-M futures trading — orders, account, balances, positions, leverage, margin type / margin movement, income history, position mode |
| `BinanceMargin` | Cross- and isolated-margin trading — borrow / repay, margin orders, account, max borrowable / transferable, interest history, force liquidations, isolated transfers |
| `BinanceAccount` | Spot account info, balances, user trades |
| `BinanceDeposit` | Deposit address and deposit history |
| `BinanceWithdrawal` | Withdrawal submission and withdrawal history |
| `BinanceTransfer` | Universal asset transfers between wallets (spot, margin, futures, funding) and history |
| `BinanceEarn` | Simple Earn — flexible and locked products, subscriptions, redemptions, positions, history |
| `BinanceSubAccount` | Sub-account list, balances, spot summary, universal transfers, futures / margin account summaries, status |

Standalone (not on a class):

| Helper | What it does |
|---|---|
| `get_api_keys()`, `get_base_url()`, `get_futures_base_url()` | Read API credentials and base URLs from environment variables |
| `binance_build_request()` | Low-level HTTP / signing primitive — every method goes through this |
| `binance_backfill_klines()` | Bulk historical klines download for many symbols × intervals with CSV resume |
| `verify_symbol()` | Sanity-check a symbol against `exchangeInfo` before placing an order |
| `time_convert_to_binance()`, `time_convert_from_binance()` | Millisecond timestamps ↔ `POSIXct` |

---

## Setup

Set credentials in `.Renviron`:

```bash
BINANCE_API_KEY=your-api-key
BINANCE_API_SECRET=your-api-secret
BINANCE_API_ENDPOINT=https://api.binance.com           # spot / margin / Earn / sub-account
BINANCE_FUTURES_API_ENDPOINT=https://fapi.binance.com  # USDⓈ-M futures
```

Then in R:

```r
library(binance)
keys     <- get_api_keys()
market   <- BinanceMarketData$new()                 # public, no keys needed
acct     <- BinanceAccount$new(keys = keys)
trading  <- BinanceTrading$new(keys = keys)
futures  <- BinanceFutures$new(keys = keys)
margin   <- BinanceMargin$new(keys = keys)
earn     <- BinanceEarn$new(keys = keys)
```

---

## `BinanceMarketData` — spot public market data

### Reference data and clock

| Method | Endpoint | Shape |
|---|---|---|
| `get_server_time()` | `/api/v3/time` | single row |
| `get_exchange_info(symbol)` | `/api/v3/exchangeInfo` | one row per symbol, `;`-collapsed string arrays (`order_types`, `permissions`, `allowed_self_trade_prevention_modes`, …); flattened numeric filters (`lot_min_qty`, `lot_max_qty`, `lot_step_size`, `price_min`, `price_max`, `price_tick_size`, `min_notional`); full filters array preserved as JSON in `filters_raw`; `permission_sets` JSON-encoded |
| `get_rate_limits()` | `/api/v3/exchangeInfo` (`rateLimits` slice) | one row per rate-limit rule |
| `get_exchange_filters()` | `/api/v3/exchangeInfo` (`exchangeFilters` slice) | one row per exchange-wide filter (usually empty) |

### Tickers and 24hr stats

| Method | Endpoint | Shape |
|---|---|---|
| `get_ticker(symbol)` | `/api/v3/ticker/price` | single row |
| `get_all_tickers()` | `/api/v3/ticker/price` | one row per symbol |
| `get_book_ticker(symbol)` | `/api/v3/ticker/bookTicker` | single row |
| `get_24hr_stats(symbol)` | `/api/v3/ticker/24hr` | single row |
| `get_all_24hr_stats()` | `/api/v3/ticker/24hr` | one row per symbol |
| `get_avg_price(symbol)` | `/api/v3/avgPrice` | single row |

### Orderbook, recent trades, klines

| Method | Endpoint | Shape |
|---|---|---|
| `get_depth(symbol, limit)` | `/api/v3/depth` | one row per `(side, price level)` — `side ∈ {"bid","ask"}`, `level` 1-indexed |
| `get_trades(symbol, limit)` | `/api/v3/trades` | one row per trade |
| `get_klines(symbol, interval, ...)` | `/api/v3/klines` | one row per kline |

```r
# Top 5 highest-priced asks
depth <- market$get_depth("BTCUSDT", limit = 5)
depth[side == "ask"][order(-price)][1:5]
```

---

## `BinanceFuturesData` — USDⓈ-M futures public market data

| Method | Endpoint | Shape |
|---|---|---|
| `get_exchange_info()` | `/fapi/v1/exchangeInfo` | one row per symbol; same string-array + filter treatment as spot (including `filters_raw`) |
| `get_rate_limits()` | `/fapi/v1/exchangeInfo` (`rateLimits` slice) | one row per rate-limit rule |
| `get_exchange_filters()` | `/fapi/v1/exchangeInfo` (`exchangeFilters` slice) | one row per exchange-wide filter (usually empty) |
| `get_futures_assets()` | `/fapi/v1/exchangeInfo` (`assets` slice) | one row per margin asset |
| `get_klines(symbol, interval, ...)` | `/fapi/v1/klines` | one row per kline |
| `get_mark_price(symbol)` | `/fapi/v1/premiumIndex` | single row (or one row per symbol if `symbol = NULL`) |
| `get_funding_rate(symbol, ...)` | `/fapi/v1/fundingRate` | one row per funding interval |
| `get_24hr_stats(symbol)` | `/fapi/v1/ticker/24hr` | single row (or one row per symbol if `symbol = NULL`) |
| `get_ticker(symbol)` | `/fapi/v1/ticker/price` | single row (or one row per symbol if `symbol = NULL`) |
| `get_book_ticker(symbol)` | `/fapi/v1/ticker/bookTicker` | single row (or one row per symbol if `symbol = NULL`) |
| `get_open_interest(symbol)` | `/fapi/v1/openInterest` | single row |
| `get_depth(symbol, limit)` | `/fapi/v1/depth` | one row per `(side, price level)` |
| `get_trades(symbol, limit)` | `/fapi/v1/trades` | one row per trade |
| `get_index_price_klines(pair, interval, ...)` | `/fapi/v1/indexPriceKlines` | one row per kline |
| `get_mark_price_klines(symbol, interval, ...)` | `/fapi/v1/markPriceKlines` | one row per kline |

---

## `BinanceMarginData` — margin reference data

| Method | Endpoint | Shape |
|---|---|---|
| `get_all_pairs()` | `/sapi/v1/margin/allPairs` | one row per cross-margin pair |
| `get_isolated_pairs()` | `/sapi/v1/margin/isolated/allPairs` | one row per isolated-margin pair |
| `get_price_index(symbol)` | `/sapi/v1/margin/priceIndex` | single row |
| `get_interest_rate_history(asset, ...)` | `/sapi/v1/margin/interestRateHistory` | one row per record |
| `get_cross_margin_data()` | `/sapi/v1/margin/crossMarginData` | one row per asset |
| `get_isolated_margin_data()` | `/sapi/v1/margin/isolatedMarginData` | one row per pair |

---

## `BinanceTrading` — spot order management

| Method | Endpoint | Shape |
|---|---|---|
| `add_order(type, symbol, side, ...)` | `POST /api/v3/order` | one row per fill if `newOrderRespType = "FULL"` and the order filled; otherwise a single row with `fill_*` columns `NA` (schema-stable) |
| `add_order_test(...)` | `POST /api/v3/order/test` | single row `data.table(validated = TRUE)` on success |
| `cancel_order(symbol, ...)` | `DELETE /api/v3/order` | single row |
| `cancel_all_orders(symbol)` | `DELETE /api/v3/openOrders` | one row per cancelled order; **empty `data.table` if no open orders** |
| `get_order(symbol, ...)` | `GET /api/v3/order` | single row |
| `get_open_orders(symbol)` | `GET /api/v3/openOrders` | one row per open order |
| `get_all_orders(symbol, ...)` | `GET /api/v3/allOrders` | one row per order |

```r
# Long format: one row per fill, parent order fields replicated.
order <- trading$add_order(
  type = "MARKET", symbol = "BTCUSDT", side = "BUY",
  quantity = 0.0001, newOrderRespType = "FULL"
)
order[, .(order_id, status, fill_index, fill_price, fill_qty)]
```

---

## `BinanceOcoOrders` — spot OCO orders

OCO lists are inherently nested (one list contains multiple legs). The
package expands the `orderReports` array to one row per leg with the
list-level fields replicated; columns are prefixed `order_report_*`.

| Method | Endpoint | Shape |
|---|---|---|
| `add_oco_order(symbol, side, ...)` | `POST /api/v3/order/oco` | one row per leg (`order_report_*` columns) |
| `cancel_oco_order(symbol, ...)` | `DELETE /api/v3/orderList` | one row per cancelled leg (`order_report_*` columns) — **not** the cut-down `orders` array Binance also returns |
| `get_oco_order(...)` | `GET /api/v3/orderList` | single row (the list itself) |
| `get_open_oco_orders()` | `GET /api/v3/openOrderList` | one row per open list |
| `get_all_oco_orders(...)` | `GET /api/v3/allOrderList` | one row per list |

---

## `BinanceFutures` — USDⓈ-M futures trading

| Method | Endpoint | Shape |
|---|---|---|
| `add_order(type, symbol, side, ...)` | `POST /fapi/v1/order` | single row |
| `add_order_test(...)` | `POST /fapi/v1/order/test` | single row `data.table(validated = TRUE)` on success |
| `cancel_order(symbol, ...)` | `DELETE /fapi/v1/order` | single row |
| `cancel_all_orders(symbol)` | `DELETE /fapi/v1/allOpenOrders` | single row |
| `get_order(symbol, ...)` | `GET /fapi/v1/order` | single row |
| `get_open_orders(symbol)` | `GET /fapi/v1/openOrders` | one row per open order |
| `get_all_orders(symbol, ...)` | `GET /fapi/v1/allOrders` | one row per order |
| `get_account()` | `GET /fapi/v2/account` | **one row per asset balance** — the `positions` array is dropped; use `get_positions()` |
| `get_balances()` | `GET /fapi/v2/balance` | one row per asset |
| `get_positions(symbol)` | `GET /fapi/v2/positionRisk` | one row per open position |
| `set_leverage(symbol, leverage)` | `POST /fapi/v1/leverage` | single row |
| `set_margin_type(symbol, marginType)` | `POST /fapi/v1/marginType` | single row |
| `modify_position_margin(symbol, ...)` | `POST /fapi/v1/positionMargin` | single row |
| `get_position_margin_history(symbol, ...)` | `GET /fapi/v1/positionMargin/history` | one row per record |
| `get_trades(symbol, ...)` | `GET /fapi/v1/userTrades` | one row per trade |
| `get_income_history(symbol, ...)` | `GET /fapi/v1/income` | one row per income record |
| `set_position_mode(dualSidePosition)` | `POST /fapi/v1/positionSide/dual` | single row |
| `get_position_mode()` | `GET /fapi/v1/positionSide/dual` | single row |

---

## `BinanceMargin` — cross- and isolated-margin trading

| Method | Endpoint | Shape |
|---|---|---|
| `add_borrow(asset, amount, ...)` | `POST /sapi/v1/margin/borrow-repay` | single row |
| `add_repay(asset, amount, ...)` | `POST /sapi/v1/margin/borrow-repay` | single row |
| `add_order(type, symbol, side, ...)` | `POST /sapi/v1/margin/order` | single row (or one row per fill, like spot) |
| `cancel_order(symbol, ...)` | `DELETE /sapi/v1/margin/order` | single row |
| `cancel_all_orders(symbol)` | `DELETE /sapi/v1/margin/openOrders` | one row per cancelled order; **empty `data.table` if no open orders** |
| `get_order(symbol, ...)` | `GET /sapi/v1/margin/order` | single row |
| `get_open_orders(symbol)` | `GET /sapi/v1/margin/openOrders` | one row per open order |
| `get_all_orders(symbol, ...)` | `GET /sapi/v1/margin/allOrders` | one row per order |
| `get_account()` | `GET /sapi/v1/margin/account` | one row per `userAsset` (account-level summary fields replicated on each row) |
| `get_max_borrowable(asset, ...)` | `GET /sapi/v1/margin/maxBorrowable` | single row (`amount`, `borrow_limit`) |
| `get_max_transferable(asset, ...)` | `GET /sapi/v1/margin/maxTransferable` | single row (`amount`, `borrow_limit`) |
| `get_interest_history(asset, ...)` | `GET /sapi/v1/margin/interestHistory` | one row per record |
| `get_force_liquidation_history(...)` | `GET /sapi/v1/margin/forceLiquidationRec` | one row per record |
| `get_trades(symbol, ...)` | `GET /sapi/v1/margin/myTrades` | one row per trade |
| `get_isolated_account(symbols)` | `GET /sapi/v1/margin/isolated/account` | one row per isolated-margin pair (account-level summary fields replicated); wide-prefixed `base_asset_*` / `quote_asset_*` |
| `add_isolated_transfer(asset, ...)` | `POST /sapi/v1/margin/isolated/transfer` | single row |

---

## `BinanceAccount` — spot account

| Method | Endpoint | Shape |
|---|---|---|
| `get_account_info()` | `GET /api/v3/account` | single row; `permissions` `;`-joined; `commissionRates` wide-prefixed (`commission_rates_*`); `balances` dropped — use `get_balances()` |
| `get_balances()` | `GET /api/v3/account` | one row per asset |
| `get_trades(symbol, ...)` | `GET /api/v3/myTrades` | one row per trade |

---

## `BinanceDeposit`

| Method | Endpoint | Shape |
|---|---|---|
| `get_deposit_address(coin, network)` | `GET /sapi/v1/capital/deposit/address` | single row |
| `get_deposit_history(coin, ...)` | `GET /sapi/v1/capital/deposit/hisrec` | one row per deposit |

## `BinanceWithdrawal`

| Method | Endpoint | Shape |
|---|---|---|
| `add_withdrawal(coin, address, amount, ...)` | `POST /sapi/v1/capital/withdraw/apply` | single row |
| `get_withdrawal_history(coin, ...)` | `GET /sapi/v1/capital/withdraw/history` | one row per withdrawal |

## `BinanceTransfer`

Universal asset transfers across spot, margin, futures, and funding
wallets.

| Method | Endpoint | Shape |
|---|---|---|
| `add_transfer(type, asset, amount, ...)` | `POST /sapi/v1/asset/transfer` | single row |
| `get_transfer_history(type, ...)` | `GET /sapi/v1/asset/transfer` | one row per record |

---

## `BinanceEarn` — Simple Earn

Flexible products and locked products have different field sets;
locked products carry extra nested objects (`detail`, `quota`) that
are flattened with a wide prefix.

### Catalogue

| Method | Endpoint | Shape |
|---|---|---|
| `get_flexible_products(asset, ...)` | `/sapi/v1/simple-earn/flexible/list` | one row per product; `tier_annual_percentage_rate` JSON-encoded (dynamic keys) |
| `get_locked_products(asset, ...)` | `/sapi/v1/simple-earn/locked/list` | one row per product; `detail_*` and `quota_*` wide-prefixed |
| `get_flexible_position(productId, asset, ...)` | `/sapi/v1/simple-earn/flexible/position` | one row per position; `tier_annual_percentage_rate` JSON-encoded |
| `get_locked_position(positionId, ...)` | `/sapi/v1/simple-earn/locked/position` | one row per position |
| `add_flexible_subscription(productId, amount, ...)` | `POST /sapi/v1/simple-earn/flexible/subscribe` | single row |
| `add_locked_subscription(projectId, amount, ...)` | `POST /sapi/v1/simple-earn/locked/subscribe` | single row |
| `add_flexible_redemption(productId, ...)` | `POST /sapi/v1/simple-earn/flexible/redeem` | single row |
| `add_locked_redemption(positionId)` | `POST /sapi/v1/simple-earn/locked/redeem` | single row |
| `get_flexible_subscription_history(...)` | `/sapi/v1/simple-earn/flexible/history/subscriptionRecord` | one row per record |
| `get_locked_subscription_history(...)` | `/sapi/v1/simple-earn/locked/history/subscriptionRecord` | one row per record |
| `get_flexible_redemption_history(...)` | `/sapi/v1/simple-earn/flexible/history/redemptionRecord` | one row per record |
| `get_locked_redemption_history(...)` | `/sapi/v1/simple-earn/locked/history/redemptionRecord` | one row per record |

```r
# Total cumulative rewards across all flexible Earn positions
earn$get_flexible_position()[
  , sum(as.numeric(cumulative_total_rewards), na.rm = TRUE)
]
```

---

## `BinanceSubAccount`

| Method | Endpoint | Shape |
|---|---|---|
| `add_sub_account(subAccountString)` | `POST /sapi/v1/sub-account/virtualSubAccount` | single row |
| `get_sub_accounts(...)` | `GET /sapi/v1/sub-account/list` | one row per sub-account |
| `get_balances(email)` | `GET /sapi/v3/sub-account/assets` | one row per asset for that sub-account |
| `get_spot_summary(email, ...)` | `GET /sapi/v1/sub-account/spotSummary` | one row per sub-account; **empty `data.table` if none** |
| `add_transfer(...)` | `POST /sapi/v1/sub-account/universalTransfer` | single row |
| `get_transfer_history(...)` | `GET /sapi/v1/sub-account/universalTransfer` | one row per record |
| `get_futures_account(email)` | `GET /sapi/v2/sub-account/futures/account` | one row per asset balance |
| `get_margin_account(email)` | `GET /sapi/v1/sub-account/margin/account` | single row (margin level + total fields); per-asset detail comes back through `BinanceMargin$get_account()` for the sub-account |
| `get_status(email)` | `GET /sapi/v1/sub-account/status` | single row |

---

## Standalone helpers

### Credentials and base URLs

```r
keys     <- get_api_keys()                      # reads .Renviron
spot_url <- get_base_url()                      # api.binance.com
fut_url  <- get_futures_base_url()              # fapi.binance.com
```

### Low-level HTTP

`binance_build_request()` constructs and signs every request. You
should rarely call it directly — every method goes through it — but
it's exported so you can wrap any not-yet-bound endpoint without
re-implementing HMAC-SHA256 signing.

### Bulk klines download

```r
# Backfill 5m bars for many symbols, with CSV resume so an aborted run
# doesn't restart from scratch.
binance_backfill_klines(
  symbols  = c("BTCUSDT", "ETHUSDT"),
  interval = "5m",
  start    = "2024-01-01",
  end      = "2024-02-01",
  output_dir = "data/klines"
)
```

### Time conversions

```r
time_convert_to_binance(as.POSIXct("2024-01-01", tz = "UTC"))
#> [1] 1704067200000
time_convert_from_binance(1704067200000)
#> [1] "2024-01-01 UTC"
```

### Symbol verification

```r
verify_symbol("BTCUSDT")   # TRUE
verify_symbol("BTCUSDC")   # TRUE
verify_symbol("FOOBAR")    # FALSE, with informative message
```

---

## Data-shape conventions

The shape policy below is shared with `alpaca` and `kucoin`. The
guiding rule is:

> **Identify the entity for the endpoint, and return one row per
> entity.**

A trade gets a row. An order gets a row. An asset balance gets a row.
A funding-rate snapshot gets a row. Anything nested under the entity
becomes a flat column on the same row or an additional row on a
different axis — **never a list column** — and **no data is dropped**;
fields that don't fit a per-entity row are surfaced via a sibling
method or as an attribute on the returned `data.table`.

There are five shape treatments. A handful of endpoints use two
treatments together when their nesting has two layers.

### Treatment A — `;` collapse for arrays of plain strings

When a field is an array of short, plain string values (codes,
permissions, order types) and the user mostly filters by them or
displays the whole list, collapse with `;` into a single character
column. Filter with `grepl`, recover the original vector with
`strsplit(x, ";", fixed = TRUE)[[1]]`.

```{r}
info <- market$get_exchange_info("BTCUSDT")

# An array of plain strings, collapsed into one `;`-separated column:
info$order_types

# Filter with grepl()
info[grepl("MARKET", order_types)]

# Recover the original vector
strsplit(info$order_types[1], ";", fixed = TRUE)[[1]]
```

Where this is used: `exchange_info` (spot + futures) for
`order_types`, `permissions`, `allowed_self_trade_prevention_modes`,
`time_in_force`, `underlying_sub_type`. `get_account_info` for
`permissions`.

The separator is `;` rather than `,` because semicolons are far less
likely to appear inside any of the joined values themselves. If
Binance ever ships a value that contains `;`, the parser emits a
once-per-session warning so we catch it immediately rather than
silently corrupting data.

### Treatment B — Long format for arrays of objects

When the array elements are themselves records (each has multiple
fields), explode to one row per element with parent fields replicated.
A 1-indexed position column is added where order matters.

```{r}
# `add_order` returns one row per fill, with the order-level fields
# replicated. `fill_index` runs 1..N.
order <- trading$add_order(
  type = "MARKET", symbol = "BTCUSDT", side = "BUY",
  quantity = 0.0001, newOrderRespType = "FULL"
)
order[, .(order_id, status, fill_index, fill_price, fill_qty)]

# `get_depth` returns one row per (side, price level).
depth <- market$get_depth("BTCUSDT", limit = 5)
depth[, .(side, price, size)]
```

Where this is used: order `fills`, OCO `orderReports`, futures account
`assets`, margin account `userAssets`, sub-account
`spotSubUserAssetBtcVoList`, orderbook `bids` / `asks`, margin
`marginablePairs`.

**Schema stability**: when the array is empty, the `<child>_` columns
are still present on the row, filled with `NA`. So
`if (any(dt$fill_index == 1L, na.rm = TRUE)) { ... }` works whether
the order had fills or not.

### Treatment C — Wide prefix for fixed-schema nested objects

When the field is a single nested object with a known fixed key set,
flatten it to `parent_child` columns.

```{r}
info <- acct$get_account_info()

# `commissionRates` was a nested object — now wide-prefixed.
info[, .(commission_rates_maker, commission_rates_taker,
         commission_rates_buyer, commission_rates_seller)]
```

Where this is used: `get_account_info`'s `commissionRates`, Earn
`get_locked_products`' `detail_*` / `quota_*`, the extracted numeric
filter columns on `exchange_info` (`lot_min_qty`, `lot_max_qty`,
`lot_step_size`, `price_min`, `price_max`, `price_tick_size`,
`min_notional`), isolated-margin `base_asset_*` / `quote_asset_*`.

### Treatment D — Re-route to a sibling method

When a response bundles a collection that doesn't fit the per-entity
row of the calling endpoint — typically heterogeneous siblings (e.g.
account-level fields **and** balances, or per-symbol rows **and**
exchange-wide rate-limit rules) — the parser keeps only the rows for
the entity the method names, and the rest is exposed via a dedicated
sibling method. Every method still returns one `data.table`; no data
is lost.

```{r}
# `BinanceFutures::get_account` returns one row per asset balance.
# Binance also returns a `positions` array alongside `assets`; rather
# than Cartesian-joining them, `positions` is parsed by the dedicated
# method that hits `/fapi/v2/positionRisk`:
fut_acct  <- futures$get_account()    # one row per asset
positions <- futures$get_positions()  # one row per open position
fut_acct
```

```{r}
# `/exchangeInfo` bundles per-symbol rows + exchange-wide rate-limit
# rules + exchange-wide filter rules. Per-symbol stays on the main
# method; the rest moves to siblings.
info        <- market$get_exchange_info()       # one row per symbol
rate_limits <- market$get_rate_limits()         # one row per rate-limit rule
ex_filters  <- market$get_exchange_filters()    # one row per exchange-wide filter (usually empty)
info
```

The cases:

- `BinanceFutures::get_account()` re-routes `positions` to
  `get_positions()`.
- `BinanceAccount::get_account_info()` re-routes `balances` to
  `get_balances()` (both methods hit `/api/v3/account`; they just
  parse different halves of the response).
- `get_exchange_info()` (spot + futures) re-routes `rateLimits` to
  `get_rate_limits()`, `exchangeFilters` to `get_exchange_filters()`,
  and (futures only) `assets` to `get_futures_assets()`. The constant
  scalars (`timezone = "UTC"`, `futuresType = "U_M"`) and `serverTime`
  (already in `get_server_time()`) are not re-exposed.

### Treatment E — JSON string for dynamic-key or array-of-array objects

When a nested object has dynamic keys (different products have
different key sets) or is an array of arrays where the inner grouping
carries semantic meaning, neither `;`-collapse nor wide-prefix
preserves the structure. Serialise the whole field as a JSON string;
recover with `jsonlite::fromJSON`.

```{r}
# spot exchangeInfo `permissionSets` is an array of arrays — each
# inner array is an alternative permission set the user can satisfy.
# `;`-joining would collapse `[["A","B"]]` and `[["A"],["B"]]` to
# the same `"A;B"`, losing the grouping.
info <- market$get_exchange_info("BTCUSDT")
info$permission_sets

# Recover the structure
jsonlite::fromJSON(info$permission_sets[1], simplifyVector = FALSE)
```

```{r}
# Earn `tierAnnualPercentageRate` has dynamic keys per product
# (different size tiers).
products <- earn$get_flexible_products(asset = "USDT")
products$tier_annual_percentage_rate

tiers <- jsonlite::fromJSON(products$tier_annual_percentage_rate[1])
tiers
```

Where this is used: spot `exchangeInfo` `permission_sets`, Earn
`get_flexible_products` / `get_flexible_position`'s
`tier_annual_percentage_rate`.

## Two cross-cutting rules

These apply to every shape treatment:

1. **Empty / null array → `NA_character_`** (no list cells). An
   asset with no `attributes` returns `attributes = NA`, not
   `attributes = list()`.
2. **Empty response → empty `data.table`** (no synthetic stub rows).
   `cancel_all_orders()` with no open orders returns a zero-row
   table, not a 1-row `(symbol, status = "cancelled")` fabrication.
   The absence of an error is the success signal.

## What was *not* done

A few intentional non-goals, mirroring the alpaca package:

- **No automatic numeric coercion of "string-numeric" fields.**
  Binance returns prices, quantities, and commissions as
  fixed-precision strings; the package preserves them as character
  so the user controls precision. Cast with `as.numeric()` at the
  point of use.
- **No automatic local-time conversion.** Timestamps come back as
  UTC `POSIXct`. Convert with `format(x, tz = "America/New_York")`
  or similar at display time.
- **No client-side rate-limiting.** The package surfaces Binance's
  `X-MBX-USED-WEIGHT` headers in errors but does not back off on its
  own — that is the caller's job.
- **No reconnect / retry on transient network errors.** The single
  call is what you asked for; wrap with `httr2::req_retry()` (passed
  through `binance_build_request()`) if you want retries.

## Why this matters across exchanges

The `alpaca`, `binance`, and (in-progress) `kucoin` packages all
follow the same shape rule. That means once you've learned
`data.table` idioms for one of them, the same idioms work on the
others — pivot a portfolio's mark-prices across both exchanges with
a straight `rbind` plus an `exchange` column, no per-source shape
massage.

```r
# Combine spot + futures + margin balances into one ledger
ledger <- rbind(
  acct$get_balances()[,         wallet := "spot"],
  futures$get_balances()[,      wallet := "usdtm"],
  margin$get_account()[,        wallet := "margin"],
  fill = TRUE
)
ledger[as.numeric(free) > 0]
```

## See also

- `vignette("getting-started", package = "binance")` — guided walk
  through placing a paper order, querying balances, and downloading
  history.
- `vignette("async-usage", package = "binance")` — using the same
  methods with `async = TRUE`.
- The README "Design Philosophy" section — short summary of the same
  convention plus the explicit per-endpoint drop list.
- The sister `alpaca` package — same convention applied to a
  different exchange.
