---
title: "Data shapes and the one-row-per-entity convention"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data shapes and the one-row-per-entity convention}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(eval = FALSE, collapse = TRUE, comment = "#>")
```

## The rule

Every `binance` method that returns nested API data follows one rule:

> **Identify the entity for the endpoint, and return one row per entity.**

A trade gets a row. An order gets a row. An asset balance gets a row.
An option contract gets a row. Anything nested under the entity becomes
a flat column on the same row or an additional row on a different axis
— **never a list column**.

The same rule applies in the sister `alpaca` and `kucoin` packages, so
that switching between exchanges doesn't mean switching mental models
of how the data looks.

## The five shape treatments

There are five shapes a nested API field can take, and five treatments.
A few endpoints use two treatments when their nesting has two layers.

### Treatment A — `;` collapse for arrays of plain strings

When a field is an array of short, plain string values (codes,
permissions, order types) and the user mostly filters by them or
displays the whole list, collapse with `;` into a single character
column. Filter with `grepl`, recover the original vector with
`strsplit(x, ";", fixed = TRUE)[[1]]`.

```{r}
market <- BinanceMarketData$new()
info <- market$get_exchange_info("BTCUSDT")

info$order_types
#> "LIMIT;LIMIT_MAKER;MARKET;STOP_LOSS_LIMIT;TAKE_PROFIT_LIMIT"

# Filter
info[grepl("MARKET", order_types)]

# Recover the vector
strsplit(info$order_types[1], ";", fixed = TRUE)[[1]]
#> "LIMIT" "LIMIT_MAKER" "MARKET" "STOP_LOSS_LIMIT" "TAKE_PROFIT_LIMIT"
```

Where this is used: `exchange_info` (spot + futures) for
`order_types`, `permissions`, `allowed_self_trade_prevention_modes`,
`time_in_force`, `underlying_sub_type`, and (futures only)
`permission_sets`. `get_account_info` for `permissions`.

The separator is `;` rather than `,` because semicolons are far less
likely to appear inside any of the joined values themselves. If
Binance ever ships a value that contains `;`, the parser emits a
once-per-session warning so we catch it immediately rather than
silently corrupting data.

### Treatment B — Long format for arrays of objects

When the array elements are themselves records (each has multiple
fields), explode to one row per element with parent fields replicated.
A 1-indexed position column is added where order matters.

```{r}
# `add_order` returns one row per fill, with the order-level fields
# replicated. `fill_index` runs 1..N.
trading <- BinanceTrading$new()
order <- trading$add_order(
  type = "MARKET", symbol = "BTCUSDT", side = "BUY",
  quantity = 0.0001, newOrderRespType = "FULL"
)
order[, .(order_id, status, fill_index, fill_price, fill_qty)]
#>    order_id  status  fill_index  fill_price  fill_qty
#> 1: 28        FILLED  1           50000.00    0.00005000
#> 2: 28        FILLED  2           50001.00    0.00005000

# `get_depth` returns one row per (side, price level).
depth <- market$get_depth("BTCUSDT", limit = 5)
depth[, .(side, price, size)]
```

Where this is used: order `fills`, OCO `orderReports`, futures account
`assets`, margin account `userAssets`, sub-account
`spotSubUserAssetBtcVoList`, orderbook `bids` / `asks`, margin
`marginablePairs`.

**Schema stability**: when the array is empty, the `<child>_` columns
are still present on the row, filled with `NA`. So
`if (any(dt$fill_index == 1L, na.rm = TRUE)) { ... }` works whether
the order had fills or not.

### Treatment C — Wide prefix for fixed-schema nested objects

When the field is a single nested object with a known fixed key set,
flatten it to `parent_child` columns.

```{r}
account <- BinanceAccount$new()
info <- account$get_account_info()

# `commissionRates` was a nested object — now wide-prefixed.
info[, .(commission_rates_maker, commission_rates_taker,
         commission_rates_buyer, commission_rates_seller)]
```

Where this is used: `get_account_info`'s `commissionRates`, Earn
`get_locked_products`' `detail_*` / `quota_*`, the extracted numeric
filter columns on `exchange_info` (`lot_min_qty`, `lot_max_qty`,
`lot_step_size`, `price_min`, `price_max`, `price_tick_size`,
`min_notional`).

### Treatment D — Drop and document

When a response includes a nested collection that doesn't fit the
one-row-per-entity shape — typically because the entity in question
already has its own dedicated endpoint — drop it and point at the
proper method.

```{r}
# `BinanceFutures::get_account` returns one row per asset balance.
# Binance also returns a `positions` array alongside `assets`, but
# they're heterogeneous — combining them would require a Cartesian
# join no user expects. So `positions` is dropped here; use the
# dedicated method:
futures <- BinanceFutures$new()
acct <- futures$get_account()       # one row per asset
positions <- futures$get_positions() # one row per open position
```

Other examples:

- `get_account_info()` drops `balances` (use `get_balances()`).
- spot / futures `exchange_info` drop top-level `rateLimits`,
  `exchangeFilters`, and (spot) `sors`. Those describe the exchange,
  not the per-symbol entity each row represents.

All deliberate drops are listed in the README's Design Philosophy
section.

### Treatment E — JSON string for dynamic-key or array-of-array objects

When a nested object has dynamic keys (different products have
different key sets) or is an array of arrays where the inner grouping
carries semantic meaning, neither `;`-collapse nor wide-prefix
preserves the structure. Serialise the whole field as a JSON string;
recover with `jsonlite::fromJSON`.

```{r}
# spot exchangeInfo `permissionSets` is an array of arrays — each
# inner array is an alternative permission set the user can satisfy.
# `;`-joining would collapse `[["A","B"]]` and `[["A"],["B"]]` to
# the same `"A;B"`, losing the grouping.
info <- market$get_exchange_info("BTCUSDT")
info$permission_sets
#> '[["SPOT","MARGIN","TRD_GRP_004", ...]]'

# Recover the structure
jsonlite::fromJSON(info$permission_sets[1], simplifyVector = FALSE)
#> [[1]]
#> [[1]][[1]] "SPOT"
#> [[1]][[2]] "MARGIN"
#> [[1]][[3]] "TRD_GRP_004"
```

```{r}
# Earn `tierAnnualPercentageRate` has dynamic keys per product
# (different size tiers).
earn <- BinanceEarn$new()
products <- earn$get_flexible_products(asset = "USDT")
products$tier_annual_percentage_rate
#> '{"0-5BTC":0.05,"5-10BTC":0.03}'

tiers <- jsonlite::fromJSON(products$tier_annual_percentage_rate[1])
tiers$`0-5BTC`
#> 0.05
```

Where this is used: spot `exchangeInfo` `permission_sets`, Earn
`get_flexible_products` / `get_flexible_position`'s
`tier_annual_percentage_rate`.

## Two cross-cutting rules

These apply to every shape treatment:

1. **Empty / null array → `NA_character_`** (no list cells). An
   asset with no `attributes` returns `attributes = NA`, not
   `attributes = list()`.
2. **Empty response → empty `data.table`** (no synthetic stub rows).
   `cancel_all_orders()` with no open orders returns a zero-row
   table, not a 1-row `(symbol, status = "cancelled")` fabrication.
   The absence of an error is the success signal.

## Why this shape works for `data.table`

`data.table` is fast and ergonomic on rectangular long-format data.
List columns make filtering, grouping, joining, and writing to disk
awkward. The convention above is what lets you write:

```{r}
# Top 5 highest-priced asks in the book
depth[side == "ask"][order(-price)][1:5]

# All BTCUSDT orders that filled at >50,000
orders <- trading$get_all_orders("BTCUSDT")
orders[as.numeric(fill_price) > 50000]

# Total cumulative rewards across all flexible Earn positions
earn$get_flexible_position()[, sum(as.numeric(cumulative_total_rewards),
                                   na.rm = TRUE)]
```

…without escape hatches into `lapply` over hidden lists.

## See also

- `vignette("getting-started", package = "binance")` — the package
  tour.
- `vignette("async-usage", package = "binance")` — using the same
  methods with `async = TRUE`.
- The README "Design Philosophy" section — short summary of the same
  convention plus the explicit per-endpoint drop list.
- The sister `alpaca` package — same convention applied to a
  different exchange.
