---
title: "Getting Started with binance"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with binance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

box::use(
  binance[
    BinanceMarketData, BinanceTrading, BinanceAccount,
    BinanceDeposit, BinanceWithdrawal, get_api_keys
  ]
)

box::use(../tests/testthat/mock_router[mock_router])

KEYS <- get_api_keys(
  api_key = "fake-key",
  api_secret = "fake-secret"
)
BASE <- "https://api.binance.com"

options(httr2_mock = mock_router)
```

This vignette demonstrates how to use `binance` in **synchronous** mode.

## Setup

```{r load}
box::use(
  binance[
    BinanceMarketData, BinanceTrading, BinanceAccount,
    BinanceDeposit, BinanceWithdrawal, get_api_keys
  ]
)

keys <- get_api_keys(
  api_key = "your-api-key",
  api_secret = "your-api-secret"
)
```

```{r keys, echo = FALSE}
keys <- KEYS
base <- BASE
```

---

## Market Data

The `BinanceMarketData` class covers all public (no auth) market endpoints.

```{r market-init}
market <- BinanceMarketData$new()
```

```{r market-init-hidden, echo = FALSE}
market <- BinanceMarketData$new(keys = keys, base_url = base)
```

### Exchange Info

```{r exchange-info}
info <- market$get_exchange_info("BTCUSDT")
info[, .(symbol, status, base_asset, quote_asset)]
```

### Ticker

```{r ticker}
ticker <- market$get_ticker("BTCUSDT")
ticker
```

### Klines (Candlestick Data)

```{r klines}
klines <- market$get_klines("BTCUSDT", "1h", limit = 5)
klines
```

### Order Book Depth

```{r orderbook}
depth <- market$get_depth("BTCUSDT", limit = 5)
depth
```

### 24hr Statistics

```{r stats-24hr}
stats <- market$get_24hr_stats("BTCUSDT")
stats[, .(symbol, last_price, price_change_percent, volume)]
```

---

## Trading

The `BinanceTrading` class manages spot orders. All trading endpoints
require authentication.

### Place a Test Order

Test orders validate parameters without executing:

```{r trading-test-order}
trading <- BinanceTrading$new()
```

```{r trading-init-hidden, echo = FALSE}
trading <- BinanceTrading$new(keys = keys, base_url = base)
```

```{r}
result <- trading$add_order_test(
  type = "LIMIT",
  symbol = "BTCUSDT",
  side = "BUY",
  price = 50000,
  quantity = 0.0001
)
result
```

### Query an Order

```{r query-order}
order <- trading$get_order("BTCUSDT", orderId = 12345)
order
```

### Get Open Orders

```{r open-orders}
open_orders <- trading$get_open_orders("BTCUSDT")
open_orders
```

---

## Account Management

### Account Info

```{r account-info}
account <- BinanceAccount$new()
```

```{r account-hidden, echo = FALSE}
account <- BinanceAccount$new(keys = keys, base_url = base)
```

```{r}
info <- account$get_account_info()
info[, .(maker_commission, taker_commission, can_trade, account_type)]
```

### Trade History

```{r trade-history}
trades <- account$get_trades("BTCUSDT")
trades
```

---

## Deposits

### Get Deposit Address

```{r deposit-address}
deposit <- BinanceDeposit$new()
```

```{r deposit-hidden, echo = FALSE}
deposit <- BinanceDeposit$new(keys = keys, base_url = base)
```

```{r}
addr <- deposit$get_deposit_address(coin = "BTC")
addr
```

### Deposit History

```{r deposit-history}
history <- deposit$get_deposit_history(coin = "BTC")
history
```

---

## Withdrawals

```{r withdrawal-init}
withdrawal <- BinanceWithdrawal$new()
```

```{r withdrawal-hidden, echo = FALSE}
withdrawal <- BinanceWithdrawal$new(keys = keys, base_url = base)
```

### Withdrawal History

```{r withdrawal-history}
history <- withdrawal$get_withdrawal_history(coin = "USDT")
history
```

### Submit a Withdrawal

```{r, eval = FALSE}
result <- withdrawal$add_withdrawal(
  coin = "USDT",
  address = "your-trc20-address",
  amount = 10,
  network = "TRX"
)
result
```

---

## Next Steps

- See the [pkgdown site](https://dereckmezquita.github.io/binance/) for full method documentation.
- For futures trading, see `BinanceFutures` and `BinanceFuturesData`.
- For margin trading, see `BinanceMargin` and `BinanceMarginData`.
