---
title: "Getting Started with binance"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with binance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>"
)

box::use(
  binance[
    BinanceMarketData, BinanceTrading, BinanceOcoOrders,
    BinanceAccount, BinanceDeposit, BinanceWithdrawal,
    BinanceTransfer, BinanceSubAccount, BinanceEarn,
    get_api_keys, binance_backfill_klines
  ]
)

box::use(../tests/testthat/mock_router[mock_router])

KEYS <- get_api_keys(
  api_key = "fake-key",
  api_secret = "fake-secret"
)
BASE <- "https://api.binance.com"

options(httr2_mock = mock_router)
```

This vignette demonstrates how to use `binance` in **synchronous** mode.

## Setup

```{r load}
box::use(
  binance[
    BinanceMarketData, BinanceTrading, BinanceOcoOrders,
    BinanceAccount, BinanceDeposit, BinanceWithdrawal,
    BinanceTransfer, BinanceSubAccount, BinanceEarn,
    get_api_keys
  ]
)

keys <- get_api_keys(
  api_key = "your-api-key",
  api_secret = "your-api-secret"
)
```

```{r keys, echo = FALSE}
keys <- KEYS
base <- BASE
```

---

## Market Data

The `BinanceMarketData` class covers all public (no auth) market endpoints.

```{r market-init}
market <- BinanceMarketData$new()
```

```{r market-init-hidden, echo = FALSE}
market <- BinanceMarketData$new(keys = keys, base_url = base)
```

### Exchange Info

```{r exchange-info}
info <- market$get_exchange_info(symbol = "BTCUSDT")
info[, .(symbol, status, base_asset, quote_asset)]
```

### Ticker

```{r ticker}
ticker <- market$get_ticker(symbol = "BTCUSDT")
ticker
```

### All Tickers

```{r all-tickers}
tickers <- market$get_all_tickers()
tickers
```

### Book Ticker

Best bid/ask prices and quantities:

```{r book-ticker}
book <- market$get_book_ticker(symbol = "BTCUSDT")
book
```

### Average Price

```{r avg-price}
avg <- market$get_avg_price(symbol = "BTCUSDT")
avg
```

### 24hr Statistics

```{r stats-24hr}
stats <- market$get_24hr_stats(symbol = "BTCUSDT")
stats[, .(symbol, last_price, price_change_percent, volume)]
```

### Order Book Depth

```{r orderbook}
depth <- market$get_depth(symbol = "BTCUSDT", limit = 5)
depth
```

### Recent Trades

```{r trades}
trades <- market$get_trades(symbol = "BTCUSDT")
trades
```

### Klines (Candlestick Data)

```{r klines}
klines <- market$get_klines(symbol = "BTCUSDT", interval = "1h", limit = 5)
klines[, .(datetime, open, high, low, close, volume)]
```

### Fetch All Klines (Large Date Ranges)

When you need more than 1000 candles, pass `fetch_all = TRUE`. The method pages
forward through the range — following the data and stopping at the first empty or
short page — then returns the combined result. Because Binance returns candles
from the first one on or after `startTime`, an empty leading stretch (e.g. dates
before a symbol was listed) is skipped in a **single** request rather than probed
piece by piece:

```{r fetch-all-klines}
# Fetch all 1h klines across a date range (paged automatically)
all_klines <- market$get_klines(
  symbol = "BTCUSDT",
  interval = "1h",
  start_time = as.POSIXct("2024-01-01", tz = "UTC"),
  end_time = as.POSIXct("2024-06-01", tz = "UTC"),
  fetch_all = TRUE,
  sleep = 0
)

nrow(all_klines)
head(all_klines[, .(datetime, open, high, low, close, volume)])
```

> **Note:** Large date ranges consume multiple API requests. Use the `sleep`
> parameter to respect Binance rate limits. For bulk multi-symbol downloads,
> see `?binance_backfill_klines`.

### Streaming Pages with `on_page`

For very large pulls you may not want to hold the whole result in memory. Pass an
`on_page` callback (used only when `fetch_all = TRUE`) and each page is handed to
it **as it is fetched** — nothing is accumulated, and the method returns
invisibly, so the callback owns the data (write it to disk, append to a database,
and so on):

```{r on-page-klines}
pages <- 0L
candles <- 0L

market$get_klines(
  symbol = "BTCUSDT",
  interval = "1h",
  start_time = as.POSIXct("2024-01-01", tz = "UTC"),
  end_time = as.POSIXct("2024-02-01", tz = "UTC"),
  fetch_all = TRUE,
  on_page = function(page) {
    pages <<- pages + 1L
    candles <<- candles + nrow(page)
    # e.g. data.table::fwrite(page, "klines.csv", append = TRUE)
    return(invisible(NULL))
  }
)

cat("streamed", pages, "page(s),", candles, "candle(s)\n")
```

This is exactly how `binance_backfill_klines()` writes to disk page by page, so an
interrupted download loses at most one page.

### Server Time

```{r server-time}
st <- market$get_server_time()
st
```

---

## Trading

The `BinanceTrading` class manages spot orders. All trading endpoints
require authentication.

```{r trading-init}
trading <- BinanceTrading$new()
```

```{r trading-init-hidden, echo = FALSE}
trading <- BinanceTrading$new(keys = keys, base_url = base)
```

### Place a Test Order

Test orders validate parameters without executing:

```{r test-order}
result <- trading$add_order_test(
  type = "LIMIT",
  symbol = "BTCUSDT",
  side = "BUY",
  price = 50000,
  quantity = 0.0001
)
result
```

### Place a Real Order

```{r real-order, eval = FALSE}
order <- trading$add_order(
  type = "LIMIT",
  symbol = "BTCUSDT",
  side = "BUY",
  price = 50000,
  quantity = 0.0001,
  time_in_force = "GTC"
)
order
```

### Query an Order

```{r query-order}
order <- trading$get_order(symbol = "BTCUSDT", order_id = 12345)
order
```

### Get Open Orders

```{r open-orders}
open_orders <- trading$get_open_orders(symbol = "BTCUSDT")
open_orders
```

### Cancel an Order

```{r cancel-order, eval = FALSE}
cancelled <- trading$cancel_order(symbol = "BTCUSDT", order_id = 12345)
cancelled
```

---

## OCO Orders

An OCO (One-Cancels-Other) order pairs a limit order with a stop-limit
order; when one side fills, the other is cancelled automatically.

```{r oco-init}
oco <- BinanceOcoOrders$new()
```

```{r oco-hidden, echo = FALSE}
oco <- BinanceOcoOrders$new(keys = keys, base_url = base)
```

```{r oco-place, eval = FALSE}
result <- oco$add_order(
  symbol = "BTCUSDT",
  side = "SELL",
  quantity = 0.001,
  price = 110000,          # Limit price (take profit)
  stop_price = 90000,       # Stop trigger price
  stop_limit_price = 89500,  # Stop limit price
  stop_limit_time_in_force = "GTC"
)
result
```

### Query OCO Orders

```{r oco-query}
open_oco <- oco$get_open_oco_orders()
open_oco
```

---

## Account Management

### Account Info

```{r account-init}
account <- BinanceAccount$new()
```

```{r account-hidden, echo = FALSE}
account <- BinanceAccount$new(keys = keys, base_url = base)
```

```{r account-info}
info <- account$get_account_info()
info[, .(maker_commission, taker_commission, can_trade, account_type)]
```

### Trade History

```{r trade-history}
trades <- account$get_trades(symbol = "BTCUSDT")
trades
```

---

## Deposits

```{r deposit-init}
deposit <- BinanceDeposit$new()
```

```{r deposit-hidden, echo = FALSE}
deposit <- BinanceDeposit$new(keys = keys, base_url = base)
```

### Get Deposit Address

```{r deposit-address}
addr <- deposit$get_deposit_address(coin = "BTC")
addr
```

### Deposit History

```{r deposit-history}
history <- deposit$get_deposit_history(coin = "BTC")
history
```

---

## Withdrawals

```{r withdrawal-init}
withdrawal <- BinanceWithdrawal$new()
```

```{r withdrawal-hidden, echo = FALSE}
withdrawal <- BinanceWithdrawal$new(keys = keys, base_url = base)
```

### Withdrawal History

```{r withdrawal-history}
history <- withdrawal$get_withdrawal_history(coin = "USDT")
history
```

### Submit a Withdrawal

```{r submit-withdrawal, eval = FALSE}
result <- withdrawal$add_withdrawal(
  coin = "USDT",
  address = "your-trc20-address",
  amount = 10,
  network = "TRX"
)
result
```

---

## Fund Transfers

Use `BinanceTransfer` to move assets between wallet types (spot, margin,
futures, funding).

```{r transfer-init, eval = FALSE}
transfer <- BinanceTransfer$new()
```

```{r transfer-example, eval = FALSE}
# Transfer 100 USDT from spot to futures
result <- transfer$add_transfer(
  type = "MAIN_UMFUTURE",
  asset = "USDT",
  amount = 100
)
result

# Check transfer history
history <- transfer$get_transfer_history(type = "MAIN_UMFUTURE")
history
```

---

## Simple Earn

Use `BinanceEarn` to subscribe to flexible savings products:

```{r earn-init}
earn <- BinanceEarn$new()
```

```{r earn-hidden, echo = FALSE}
earn <- BinanceEarn$new(keys = keys, base_url = base)
```

### List Available Products

```{r earn-products}
products <- earn$get_flexible_products()
products
```

### Subscribe

```{r earn-subscribe, eval = FALSE}
result <- earn$subscribe_flexible(product_id = "BTC001", amount = 0.01)
result
```

### Check Positions

```{r earn-positions}
positions <- earn$get_flexible_position()
positions
```

---

## Sub-Account Management

```{r sub-init}
sub <- BinanceSubAccount$new()
```

```{r sub-hidden, echo = FALSE}
sub <- BinanceSubAccount$new(keys = keys, base_url = base)
```

```{r sub-list}
subs <- sub$get_sub_accounts()
subs
```

---

## Clock Drift: Server Time Signing

By default, HMAC request signatures use your local machine's clock. If your
system time is out of sync with Binance's servers, authenticated requests may
fail with timestamp errors. You can configure any class to fetch the server
time before each authenticated request:

```{r clock-drift, eval = FALSE}
# Use server time for signing (adds one round trip per request)
trading <- BinanceTrading$new(time_source = "server")

# All authenticated calls now use the exchange clock
order <- trading$add_order_test(
  type = "LIMIT", symbol = "BTCUSDT", side = "BUY",
  price = 50000, quantity = 0.0001
)
```

The `time_source` parameter is available on all class constructors:
`BinanceTrading`, `BinanceAccount`, `BinanceOcoOrders`,
`BinanceDeposit`, `BinanceWithdrawal`, `BinanceTransfer`,
`BinanceSubAccount`, `BinanceMargin`, `BinanceEarn`, and `BinanceFutures`.

---

## Bulk Historical Data: Backfill Klines

Download historical kline data across multiple symbols and timeframes, written
to CSV **page by page** with automatic resume — an interrupted download loses at
most one page, and re-running continues each series from its last saved candle:

```{r backfill, eval = FALSE}
binance_backfill_klines(
  symbols = c("BTCUSDT", "ETHUSDT"),
  timeframes = c("1d", "4h"),
  from = lubridate::as_datetime("2020-01-01"),
  to = lubridate::now("UTC"),
  file = "my_klines.csv"
)

# Resume an interrupted download — just run the same call again.
# It reads the existing CSV and continues each symbol/timeframe from its last
# saved candle.
```

---

## Next Steps

- See `vignette("async-usage")` for promise-based asynchronous operation.
- See `vignette("margin-futures-trading")` for margin and USD-M futures trading.
- Browse the [pkgdown site](https://dereckscompany.github.io/binance/) for full method documentation.
- For bulk historical data, see `?binance_backfill_klines`.
