---
title: "Margin and Futures Trading with binance"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Margin and Futures Trading with binance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

box::use(../tests/testthat/mock_router[mock_router])
options(httr2_mock = mock_router)
```

This vignette covers margin and USD-M futures trading using the `binance`
package. All examples use synchronous mode and mock data so they run
without a live API connection.

## Overview

The package provides four classes for margin and futures operations:

| Class | Purpose |
|-------|---------|
| `BinanceMarginData` | Query margin pairs, price index, interest rates, cross/isolated margin data |
| `BinanceMargin` | Borrow, repay, place margin orders, query margin account |
| `BinanceFuturesData` | Futures exchange info, mark price, funding rates, klines, open interest |
| `BinanceFutures` | Place futures orders, manage positions, leverage, account queries |

---

## Setup

```{r load, eval = TRUE}
library(binance)

keys <- get_api_keys(
  api_key = "your-key",
  api_secret = "your-secret"
)

# Margin clients
margin_data <- BinanceMarginData$new(keys = keys)
margin <- BinanceMargin$new(keys = keys)

# Futures clients
futures_data <- BinanceFuturesData$new(keys = keys)
futures <- BinanceFutures$new(keys = keys)
```

---

## Margin Trading

### Available Margin Pairs

Retrieve all cross margin trading pairs to see which symbols support
margin trading:

```{r margin-pairs, eval = TRUE}
pairs <- margin_data$get_all_pairs()
print(pairs)
```

### Price Index

The margin price index is a public endpoint (no authentication
required). It returns the index price used for margin calculations:

```{r margin-price-index, eval = TRUE}
idx <- margin_data$get_price_index("BTCUSDT")
print(idx)
```

### Cross Margin Data

Query cross margin fee data including daily/yearly interest rates and
borrowing limits per coin:

```{r cross-margin-data, eval = TRUE}
cm_data <- margin_data$get_cross_margin_data()
print(cm_data)
```

### Interest Rate History

Check historical interest rates for a specific asset:

```{r interest-rate-history, eval = TRUE}
rate_history <- margin_data$get_interest_rate_history("BTC")
print(rate_history)
```

### Borrowing and Repaying

Borrow assets against your margin collateral and repay loans. These are
write operations that modify account state:

```{r borrow-repay, eval = FALSE}
# Borrow 100 USDT on cross margin
loan <- margin$add_borrow(asset = "USDT", amount = 100)
print(loan)

# Repay the loan
repay <- margin$add_repay(asset = "USDT", amount = 100)
print(repay)

# Check max borrowable amount
max_borrow <- margin$get_max_borrowable(asset = "USDT")
print(max_borrow)
```

### Placing Margin Orders

Place a limit buy order on cross margin. The `sideEffectType` parameter
controls auto-borrowing behaviour:

- `"NO_SIDE_EFFECT"` -- normal order, no auto-borrow.
- `"MARGIN_BUY"` -- auto-borrow if insufficient balance.
- `"AUTO_REPAY"` -- auto-repay after the trade fills.

```{r margin-order, eval = TRUE}
order <- margin$add_order(
  symbol = "BTCUSDT",
  side = "BUY",
  type = "LIMIT",
  quantity = 0.001,
  price = 50000,
  timeInForce = "GTC",
  sideEffectType = "MARGIN_BUY"
)
print(order)
```

Query open margin orders:

```{r margin-open-orders, eval = TRUE}
open <- margin$get_open_orders("BTCUSDT")
print(open)
```

### Margin Account Information

Get a summary of your cross margin account including margin level,
total assets, and liabilities:

```{r margin-account, eval = TRUE}
account <- margin$get_account()
print(account[, .(borrow_enabled, margin_level, total_asset_of_btc,
                   total_liability_of_btc, total_net_asset_of_btc)])
```

### Margin Trade History

Retrieve executed margin trades for a symbol:

```{r margin-trades, eval = TRUE}
trades <- margin$get_trades("BTCUSDT")
print(trades)
```

---

## Futures Trading

### Exchange Information

Retrieve futures trading pair metadata including contract type,
precision, and filters:

```{r futures-exchange-info, eval = TRUE}
info <- futures_data$get_exchange_info()
print(info[, .(symbol, contract_type, status, base_asset, quote_asset)])
```

### Mark Price and Funding Rate

The mark price is used for liquidation and unrealised PnL calculations.
Funding rates are periodic payments between long and short positions:

```{r futures-mark-price, eval = TRUE}
mark <- futures_data$get_mark_price("BTCUSDT")
print(mark)
```

```{r futures-funding-rate, eval = TRUE}
rates <- futures_data$get_funding_rate("BTCUSDT", limit = 5)
print(rates)
```

### Futures Klines

Fetch historical candlestick data for futures contracts:

```{r futures-klines, eval = TRUE}
klines <- futures_data$get_klines("BTCUSDT", interval = "1h", limit = 5)
print(klines)
```

### Open Interest

Check the total open interest for a futures symbol:

```{r futures-open-interest, eval = TRUE}
oi <- futures_data$get_open_interest("BTCUSDT")
print(oi)
```

### Futures Account and Positions

Query your futures account summary and current positions:

```{r futures-account, eval = TRUE}
account <- futures$get_account()
print(account[, .(total_initial_margin, total_maint_margin,
                   total_wallet_balance, total_unrealized_profit,
                   available_balance)])
```

```{r futures-positions, eval = TRUE}
positions <- futures$get_positions("BTCUSDT")
print(positions)
```

### Futures Balances

Retrieve per-asset balances in the futures account:

```{r futures-balances, eval = TRUE}
balances <- futures$get_balances()
print(balances)
```

### Setting Leverage

Adjust the initial leverage for a futures symbol (1-125x):

```{r futures-leverage, eval = TRUE}
result <- futures$set_leverage("BTCUSDT", leverage = 10)
print(result)
```

### Placing Futures Orders

Use the test endpoint to validate order parameters without creating a
real order:

```{r futures-order-test, eval = TRUE}
test <- futures$add_order_test(
  symbol = "BTCUSDT",
  side = "BUY",
  type = "LIMIT",
  quantity = 0.001,
  price = 50000,
  timeInForce = "GTC"
)
print(test)
```

Place a real futures order (use with caution on a live account):

```{r futures-order, eval = FALSE}
order <- futures$add_order(
  symbol = "BTCUSDT",
  side = "BUY",
  type = "LIMIT",
  quantity = 0.001,
  price = 50000,
  timeInForce = "GTC"
)
print(order)
```

Market orders require only the quantity:

```{r futures-market-order, eval = FALSE}
order <- futures$add_order(
  symbol = "BTCUSDT",
  side = "BUY",
  type = "MARKET",
  quantity = 0.001
)
print(order)
```

### Margin Type and Position Mode

Switch between crossed and isolated margin, and between one-way and
hedge mode:

```{r futures-margin-type, eval = FALSE}
# Switch to isolated margin
futures$set_margin_type("BTCUSDT", "ISOLATED")

# Enable hedge mode (dual side positions)
futures$set_position_mode(dualSidePosition = TRUE)
```

### Income History

Retrieve funding fees, realised PnL, commissions, and other income
entries:

```{r futures-income, eval = TRUE}
income <- futures$get_income_history(symbol = "BTCUSDT")
print(income)
```

### Futures Trade History

Query executed trades on the futures account:

```{r futures-trades, eval = TRUE}
trades <- futures$get_trades("BTCUSDT")
print(trades)
```

---

## Method Reference

### BinanceMarginData

| Method | Description |
|--------|-------------|
| `get_all_pairs()` | All cross margin trading pairs |
| `get_isolated_pairs()` | All isolated margin trading pairs |
| `get_price_index(symbol)` | Margin price index (public) |
| `get_interest_rate_history(asset)` | Historical interest rates |
| `get_cross_margin_data()` | Cross margin fee data |
| `get_isolated_margin_data()` | Isolated margin fee data |

### BinanceMargin

| Method | Description |
|--------|-------------|
| `add_borrow(asset, amount)` | Borrow assets on margin |
| `add_repay(asset, amount)` | Repay margin loan |
| `add_order(...)` | Place a margin order |
| `cancel_order(symbol, orderId)` | Cancel a margin order |
| `cancel_all_orders(symbol)` | Cancel all open margin orders |
| `get_order(symbol, orderId)` | Query a specific order |
| `get_open_orders(symbol)` | List open margin orders |
| `get_all_orders(symbol)` | List all margin orders |
| `get_account()` | Cross margin account info |
| `get_max_borrowable(asset)` | Max borrowable amount |
| `get_max_transferable(asset)` | Max transferable amount |
| `get_interest_history()` | Interest accrual history |
| `get_trades(symbol)` | Margin trade history |
| `get_isolated_account()` | Isolated margin account info |
| `add_isolated_transfer(...)` | Transfer between spot and isolated margin |

### BinanceFuturesData

| Method | Description |
|--------|-------------|
| `get_exchange_info()` | Futures trading pair metadata |
| `get_klines(symbol, interval)` | Historical candlestick data |
| `get_mark_price(symbol)` | Mark price, index price, funding rate |
| `get_funding_rate(symbol)` | Historical funding rates |
| `get_24hr_stats(symbol)` | 24h price change statistics |
| `get_ticker(symbol)` | Latest price ticker |
| `get_book_ticker(symbol)` | Best bid/ask prices |
| `get_open_interest(symbol)` | Current open interest |
| `get_depth(symbol)` | Order book depth |
| `get_trades(symbol)` | Recent trades |
| `get_index_price_klines(pair, interval)` | Index price klines |
| `get_mark_price_klines(symbol, interval)` | Mark price klines |

### BinanceFutures

| Method | Description |
|--------|-------------|
| `add_order(...)` | Place a futures order |
| `add_order_test(...)` | Validate order without placing |
| `cancel_order(symbol, orderId)` | Cancel a futures order |
| `cancel_all_orders(symbol)` | Cancel all open futures orders |
| `get_order(symbol, orderId)` | Query a specific order |
| `get_open_orders(symbol)` | List open futures orders |
| `get_all_orders(symbol)` | List all futures orders |
| `get_account()` | Futures account info |
| `get_balances()` | Per-asset balances |
| `get_positions(symbol)` | Position risk info |
| `set_leverage(symbol, leverage)` | Set initial leverage (1-125x) |
| `set_margin_type(symbol, marginType)` | Set crossed or isolated margin |
| `modify_position_margin(symbol, amount, type)` | Add or reduce position margin |
| `get_trades(symbol)` | Futures trade history |
| `get_income_history(symbol)` | Income history (funding, PnL, etc.) |
| `set_position_mode(dualSidePosition)` | Switch one-way / hedge mode |
| `get_position_mode()` | Query current position mode |
