---
title: "Live WebSocket Streams with binance"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Live WebSocket Streams with binance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  eval = FALSE
)
```

The REST classes (e.g. [`BinanceMarketData`]) give you a *snapshot* — the order
book at the instant you ask. The WebSocket classes give you the *stream* — every
change as it happens. Binance only archives snapshots, so the live order-book
diff stream is the one piece of market data that is lost forever if you do not
record it.

`binance` exposes streams with a **Node.js-style event API**: you register a
handler and the library calls it as messages arrive. This is the same shape as
JavaScript's `ws.on("message", ...)` and as Binance's own official connectors.

> Built on the `websocket` (the client) and `later` (R's libuv event loop)
> packages — both hard dependencies of `binance`, so they are already installed.

## The event API

```{r api}
box::use(binance[BinanceMarketStream])

stream <- BinanceMarketStream$new()

# ws.on("message", ...) — handlers receive the RAW JSON string
stream$on("message", function(msg) cat(msg, "\n"))

stream$depth("BTCUSDT", speed = "100ms") # subscribe to the order-book diff stream
stream$run()                             # keep the process alive; interrupt to stop
```

`$run()` is the only thing R needs that Node gives for free — see
**Driving the event loop** below for what it does and when to drive the loop
yourself instead.

## No `async` flag (unlike the REST classes)

A REST call has a single result, so it can be synchronous (returns a value) or
asynchronous (returns a promise). A socket is an **endless push stream** with no
single result — so the only sensible shape is a callback, and there is nothing
to dualise. Streams are always event-driven.

## Driving the event loop: two ways

The class never owns the loop — `$on()`, `$connect()`, and `$depth()` just register
callbacks on `later` and return immediately. *Something* has to pump `later` so
those callbacks fire (R has no always-on loop like Node.js). You have two options.

### 1. Drive the loop yourself — recommended when embedding

Register your handlers, `$connect()` (non-blocking), then pump `later::run_now()`:

```{r external}
stream <- BinanceMarketStream$new()
stream$on("message", function(msg) record(msg))
stream$depth("BTCUSDT", speed = "100ms")
stream$connect() # non-blocking: wires up + starts connecting, returns immediately

while (!later::loop_empty()) later::run_now(0.1) # you own the loop
```

This is the right approach when the client lives **inside a program that already
runs a `later` loop** — a Shiny app, or a trading engine that also drives REST
promises, timers, and other components on the same loop. There you don't even
write the loop: just `$connect()`, and the host loop fires your handlers alongside
everything else. Driving the loop yourself also lets you do your own work each
tick, add other tasks, or set your own stop condition.

### 2. `$run()` — syntactic sugar for a standalone recorder

When the client is the *only* thing running, `$run()` connects, pumps the loop, and
tears down cleanly for you:

```{r helper}
stream$run() # = connect() + pump later::run_now() + clean close on Ctrl-C / error
```

`$run()` is approach 1 wrapped up, plus guaranteed teardown: a normal close, an
error, or an **interrupt (Ctrl-C)** all close the socket and cancel timers on the
way out (via `on.exit()`), so you never leave a half-open connection.

## Recording the order book to disk

The order book is a firehose; write it compressed, one file per symbol per day,
and let a separate step turn it into Parquet later. The recorder itself is tiny:

```{r recorder}
box::use(binance[BinanceMarketStream])

con <- gzfile("btcusdt-depth.ndjson.gz", open = "ab")
on.exit(close(con))

stream <- BinanceMarketStream$new()
stream$on("message", function(msg) cat(msg, "\n", file = con, sep = ""))
stream$depth("BTCUSDT", speed = "100ms")
stream$run()
```

The raw message is written verbatim — faithful bronze data from which the full
book can be reconstructed later.

## Many symbols, one connection

Up to 1024 streams share a single connection, so recording 100 order books is
one socket, not 100. Just subscribe to each:

```{r multi}
stream <- BinanceMarketStream$new()
stream$on("message", function(msg) write_somewhere(msg))
for (sym in c("BTCUSDT", "ETHUSDT", "SOLUSDT")) {
  stream$depth(sym, speed = "100ms")
}
stream$run()
```

## Reconnection is automatic

You do not manage reconnection. On an unexpected disconnect the client reconnects
with exponential backoff (plus jitter, so it can never trip Binance's
connection-rate limit), reconnects proactively at 23 hours to beat Binance's
24-hour forced disconnect, and re-subscribes every stream after reconnecting.
If reconnects are exhausted, `$run()` returns — so an external supervisor (a
cron + lock, a container restart policy) can bring the recorder back.

```{r reconnect}
stream <- BinanceMarketStream$new(max_reconnects = 10) # then $run() returns; let the supervisor restart
```

## Stopping

Interrupt the session (Ctrl-C), or call `stream$close()` from a handler — that
stops auto-reconnect, cancels timers, closes the socket, and `$run()` returns.
