---
title: "Live WebSocket Streams with binance"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Live WebSocket Streams with binance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  eval = FALSE
)
```

The REST classes (e.g. [`BinanceMarketData`]) give you a *snapshot* — the order
book at the instant you ask. The WebSocket classes give you the *stream* — every
change as it happens. Binance only archives snapshots, so the live order-book
diff stream is the one piece of market data that is lost forever if you do not
record it.

`binance` exposes streams with a **Node.js-style event API**: you register a
handler and the library calls it as messages arrive. This is the same shape as
JavaScript's `ws.on("message", ...)` and as Binance's own official connectors.

> Requires the `websocket` and `later` packages: `install.packages(c("websocket", "later"))`.

## The event API

```{r api}
box::use(binance[BinanceMarketStream])

stream <- BinanceMarketStream$new()

# ws.on("message", ...) — handlers receive the RAW JSON string
stream$on("message", function(msg) cat(msg, "\n"))

stream$depth("BTCUSDT", speed = "100ms") # subscribe to the order-book diff stream
stream$run()                             # keep the process alive; interrupt to stop
```

`$run()` is the only thing R needs that Node gives for free — see the event-loop
note below.

## No `async` flag (unlike the REST classes)

A REST call has a single result, so it can be synchronous (returns a value) or
asynchronous (returns a promise). A socket is an **endless push stream** with no
single result — so the only sensible shape is a callback, and there is nothing
to dualise. Streams are always event-driven.

> **Event loop.** R has no always-on event loop like Node.js. Handlers only fire
> when the loop ticks via `later::run_now()`. `$run()` does this for you — it
> connects, then pumps `later::run_now()` until you close the client, so the
> process stays alive while the socket is open (exactly how Node keeps a process
> alive). Inside **Shiny** or another running loop, you do not call `$run()` —
> register your handlers and the existing loop fires them.

## Recording the order book to disk

The order book is a firehose; write it compressed, one file per symbol per day,
and let a separate step turn it into Parquet later. The recorder itself is tiny:

```{r recorder}
box::use(binance[BinanceMarketStream])

con <- gzfile("btcusdt-depth.ndjson.gz", open = "ab")
on.exit(close(con))

stream <- BinanceMarketStream$new()
stream$on("message", function(msg) cat(msg, "\n", file = con, sep = ""))
stream$depth("BTCUSDT", speed = "100ms")
stream$run()
```

The raw message is written verbatim — faithful bronze data from which the full
book can be reconstructed later.

## Many symbols, one connection

Up to 1024 streams share a single connection, so recording 100 order books is
one socket, not 100. Just subscribe to each:

```{r multi}
stream <- BinanceMarketStream$new()
stream$on("message", function(msg) write_somewhere(msg))
for (sym in c("BTCUSDT", "ETHUSDT", "SOLUSDT")) {
  stream$depth(sym, speed = "100ms")
}
stream$run()
```

## Reconnection is automatic

You do not manage reconnection. On an unexpected disconnect the client reconnects
with exponential backoff (plus jitter, so it can never trip Binance's
connection-rate limit), reconnects proactively at 23 hours to beat Binance's
24-hour forced disconnect, and re-subscribes every stream after reconnecting.
If reconnects are exhausted, `$run()` returns — so an external supervisor (a
cron + lock, a container restart policy) can bring the recorder back.

```{r reconnect}
stream <- BinanceMarketStream$new(max_reconnects = 10) # then $run() returns; let the supervisor restart
```

## Stopping

Interrupt the session (Ctrl-C), or call `stream$close()` from a handler — that
stops auto-reconnect, cancels timers, closes the socket, and `$run()` returns.
